% ============================================================
% RESUME CONTENT - OPTIMIZED FOR SOFTWARE ENGINEER ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{Software Engineer} with 2+ years of experience building scalable applications across mobile, desktop, and web platforms. Proficient in \textbf{Python}, \textbf{C++}, \textbf{Kotlin}, \textbf{Dart}, and \textbf{TypeScript} with strong foundation in \textbf{data structures}, \textbf{algorithms}, and \textbf{system design}. Proven expertise in clean architecture, agile methodologies, and delivering production-ready solutions. Experience in mobile development (Flutter, Android, React Native), systems programming, and ML integration. Passionate about writing clean, maintainable code and solving complex engineering challenges.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Present}%
    {%
        \item Won first place in a 30+ team hackathon, earning a full-time position offer.
        \item Collaborated with back-end engineers and QA testers in an agile environment, analyzing app architecture and state management to guide feature development.
        \item Implemented offline functionality, fixed bugs, and optimized database queries for performance tuning.
        \item Developed complex SQL queries for offline database with direct backend interaction.
    }%
    |||
    {Android Developer Intern}%
    {Banque Misr}%
    {Jul 2025 - Sep 2025}%
    {%
        \item Developed native Android applications using Kotlin, Jetpack components, and Room Database.
        \item Implemented MVVM architecture patterns for scalable, maintainable mobile solutions.
    }%
    |||
    {Mobile Development Intern (Flutter \& ML)}%
    {Informatique}%
    {Jul 2025 - Aug 2025}%
    {%
        \item Integrated ML models into mobile applications using TFLite/ML Kit for on-device processing.
    }%
    |||
    {Data Science Trainee}%
    {Digital Egypt Pioneers Initiative (DEPI)}%
    {Jun 2025 - Dec 2025}%
    {%
        \item Completed IBM Data Scientist certification with Python, SQL, and machine learning.
        \item Delivered capstone project with end-to-end ML pipeline achieving 99.96\% R² accuracy.
    }%
    |||
    {Flutter Instructor}%
    {IEEE Cairo University SB}%
    {Feb 2025 - May 2025}%
    {%
        \item Instructed 30+ students in software development, state management, and API integration.
    }%
    |||
    {Flutter Developer Intern}%
    {SlashHub}%
    {Oct 2024 - Jan 2025}%
    {%
        \item Designed reactive UI components for AI-powered chatbot, achieving 25\% improvement in user engagement.
    }%
    |||%
}

% PROJECTS
\newcommand{\projectsList}{%
    {Jun 2025}%
    {https://github.com/KarimmYasser/isupply_app}%
    {i'Supply POS App - First Place Hackathon Winner}%
    {Developed a cross-platform \textbf{Flutter POS system} for desktop and mobile with offline synchronization, \textbf{Hive} local storage, and \textbf{Supabase} backend, supporting 1000+ products.}%
    |||
    {Oct 2025 - Dec 2025}%
    {https://github.com/KarimmYasser/yapper-mobile}%
    {Yapper - X Clone Mobile App}%
    {Built a cross-platform \textbf{React Native} social media app with real-time \textbf{WebSocket} messaging, push notifications, RTL support, and \textbf{CI/CD} automation via EAS.}%
    |||
    {Aug 2025 - Sep 2025}%
    {https://github.com/KarimmYasser/coffee_shop}%
    {Coffee Shop Android App}%
    {Developed an offline-first Android app using \textbf{Kotlin Jetpack Compose}, \textbf{Clean Architecture} with MVVM, \textbf{Hilt}, \textbf{Room}, and \textbf{Retrofit}.}%
    |||
    {Mar 2025 – May 2025}%
    {https://github.com/KarimmYasser/sher-look}%
    {Sherlook Web Engine}%
    {Built a web search engine with custom \textbf{crawler}, \textbf{indexer}, and \textbf{ranking algorithm} processing 50K+ pages.}%
    |||
    {Feb 2025}%
    {https://github.com/KarimmYasser/cmpsh}%
    {Custom Unix Shell (cmpsh)}%
    {Implemented a Unix shell in \textbf{C} demonstrating \textbf{process management} (fork/exec), \textbf{piping}, and \textbf{I/O redirection}.}%
    |||
    {Mar 2025 – May 2025}%
    {https://github.com/KarimmYasser/kernel-sim-ohh-s}%
    {OS Process Scheduler Simulator}%
    {Simulated CPU scheduling algorithms (\textbf{FCFS}, \textbf{SJF}, \textbf{Priority}, \textbf{Round Robin}) with real-time visualization.}%
    |||
    {Nov 2025}%
    {https://github.com/KarimmYasser/Walmart-Sales-Forecasting-ML}%
    {Walmart Sales Forecasting - ML Pipeline}%
    {Built end-to-end \textbf{ML pipeline} achieving \textbf{99.96\% R²} accuracy, deployed via \textbf{FastAPI} and \textbf{Docker}.}%
    |||
    {Oct 2025 - Dec 2025}%
    {https://github.com/KarimmYasser/stall_3alda2ery}%
    {5-Stage Pipelined Processor}%
    {Designed a 32-bit pipelined processor in \textbf{VHDL} with hazard handling and custom \textbf{Python} assembler.}%
    |||
    {Feb 2024 – Apr 2024}%
    {https://github.com/KarimmYasser/Alien_Invasion_Project}%
    {Alien Invasion Simulator}%
    {Implemented an alien invasion simulator in \textbf{C++} with custom \textbf{data structures} and \textbf{OOP design patterns}.}%
    |||%
}

% TECHNICAL SKILLS
\newcommand{\programmingLanguages}{
Python,
C++,
C,
Kotlin,
Dart,
Java,
TypeScript,
JavaScript,
SQL
}

\newcommand{\mobileDevelopment}{
Flutter (Mobile \& Desktop),
Android Development (Kotlin, Jetpack Compose),
React Native (Expo),
Cross-platform Development
}

\newcommand{\frameworksLibraries}{
Flutter Bloc,
Riverpod,
Dagger/Hilt,
Room,
Retrofit,
Firebase,
RESTful APIs,
FastAPI,
Scikit-learn,
Pandas,
NumPy
}

\newcommand{\backendDatabase}{
Supabase,
Firebase,
MySQL,
PostgreSQL,
SQLite,
Room,
Database Design,
Offline-first Architecture,
API Integration
}

\newcommand{\developmentTools}{
Git,
GitHub,
Docker,
Linux,
VS Code,
Android Studio,
Jupyter Notebooks,
CI/CD,
Agile/Scrum
}

\newcommand{\softwareEngineering}{
Clean Architecture,
MVVM,
SOLID Principles,
Dependency Injection,
State Management,
Object-Oriented Programming (OOP),
Design Patterns,
Test-Driven Development
}

\newcommand{\dataScience}{
Data Structures,
Algorithms,
Machine Learning,
Data Analysis
}

\newcommand{\artificialIntelligence}{
ML Integration (TFLite/ML Kit),
Supervised Learning,
Feature Engineering
}

\newcommand{\researchSkills}{
Technical Documentation,
Code Review,
System Design
}

\newcommand{\specializedSkills}{
Operating Systems,
Systems Programming,
Process Management,
Computer Architecture,
FPGA,
Verilog/VHDL
}

% CORE COMPETENCIES
\newcommand{\problemSolving}{
Analytical thinking,
Problem decomposition,
Algorithm design,
Debugging,
Root cause identification
}

\newcommand{\leadership}{
Technical mentoring,
Code review,
Cross-functional collaboration,
Agile teamwork
}

\newcommand{\communication}{
Technical documentation,
Knowledge transfer,
Remote collaboration
}

\newcommand{\continuousLearning}{
Technology adoption,
Industry best practices,
Rapid skill acquisition,
Self-directed learning
}

% ============================================================
