% ============================================================
% RESUME CONTENT - OPTIMIZED FOR AI ENGINEER ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{AI Engineer} with hands-on experience integrating AI/ML solutions into production applications. IBM certified with expertise in \textbf{Python}, \textbf{TensorFlow}, \textbf{HuggingFace}, and \textbf{NLP}. Experience deploying on-device AI using TFLite/ML Kit, building chatbots with NLP integration, and implementing recommendation systems. Strong foundation in MLOps, model optimization, and hardware acceleration for neural network inference. Proven ability to deliver AI-powered features that improve user engagement by 25\%.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Mobile Development Intern (Flutter \& ML)}%
    {Informatique}%
    {Jul 2025 - Aug 2025}%
    {%
        \item Integrated Machine Learning models into mobile applications for intelligent, responsive solutions.
        \item Developed cross-platform AI features using TFLite/ML Kit for on-device inference and real-time processing.
    }%
    |||
    {Data Science Trainee}%
    {Digital Egypt Pioneers Initiative (DEPI)}%
    {Jun 2025 - Dec 2025}%
    {%
        \item Completed IBM Data Scientist certification with Python and machine learning.
        \item Implemented MLOps workflows using MLflow and HuggingFace for AI model deployment.
        \item Delivered capstone project with end-to-end AI pipeline for business solutions.
    }%
    |||
    {Flutter Developer Intern}%
    {SlashHub}%
    {Oct 2024 - Jan 2025}%
    {%
        \item Designed AI-powered e-commerce chatbot with NLP integration and product recommendations.
        \item Achieved 25\% improvement in user engagement through intelligent conversation design.
    }%
    |||
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Present}%
    {%
        \item Won first place in a 30+ team hackathon, earning a full-time position offer.
        \item Collaborated in agile environment on data-driven application development.
    }%
    |||%
}

% PROJECTS
\newcommand{\projectsList}{%
    {Nov 2024 - Dec 2024}%
    {https://github.com/KarimmYasser/Slash-Fashion-Assistant-App}%
    {Fashion Assistant - AI E-commerce Platform}%
    {Built an AI-powered personalized shopping assistant with \textbf{NLP chatbot} and \textbf{product recommendation system}.}%
    |||
    {Oct 2025 - Dec 2025}%
    {https://github.com/KarimmYasser/yapper-mobile}%
    {Yapper - AI-Powered Social Media App}%
    {Built a React Native app featuring \textbf{AI-powered tweet summarization} and intelligent content processing.}%
    |||
    {Nov 2025}%
    {https://github.com/KarimmYasser/Walmart-Sales-Forecasting-ML}%
    {Walmart Sales Forecasting - AI Pipeline}%
    {Built an end-to-end \textbf{AI pipeline} achieving \textbf{99.96\% R²} accuracy, deployed via FastAPI with MLflow tracking and Docker.}%
    |||
    {Nov 2025 - Dec 2025}%
    {https://github.com/KarimmYasser/VLSI-Convolution-Systolic-Accelerator}%
    {Neural Network Hardware Accelerator}%
    {Designed a \textbf{CNN accelerator} in Verilog using systolic arrays for optimized \textbf{neural network inference}.}%
    |||
    {Sep 2025}%
    {https://github.com/KarimmYasser/heart_disease_prediction}%
    {Heart Disease AI Prediction}%
    {Engineered an AI diagnostic pipeline with feature engineering, model optimization, and interactive deployment.}%
    |||
    {Jul 2025 - Aug 2025}%
    {https://github.com/KarimmYasser/school_scheduler}%
    {AI Timetable Generator}%
    {Developed an \textbf{AI-driven} constraint satisfaction optimizer using Google OR-Tools.}%
    |||
    {Mar 2025 – May 2025}%
    {https://github.com/KarimmYasser/sher-look}%
    {Sherlook AI Search Engine}%
    {Built a search engine with \textbf{AI ranking algorithms} processing 50K+ pages.}%
    |||%
}

% TECHNICAL SKILLS
\newcommand{\programmingLanguages}{
Python,
C++,
SQL,
Java
}

\newcommand{\mobileDevelopment}{
TFLite,
ML Kit,
On-device AI,
Edge AI
}

\newcommand{\frameworksLibraries}{
TensorFlow,
PyTorch,
Hugging Face,
Transformers,
Scikit-learn,
LangChain,
FastAPI,
Streamlit
}

\newcommand{\backendDatabase}{
Vector Databases,
PostgreSQL,
MySQL,
API Integration
}

\newcommand{\developmentTools}{
Docker,
Git,
GitHub,
MLflow,
Hugging Face Hub,
Jupyter Notebooks,
VS Code
}

\newcommand{\softwareEngineering}{
AI Pipelines,
MLOps,
Model Serving,
API Development,
Microservices
}

\newcommand{\dataScience}{
Feature Engineering,
Data Preprocessing,
Model Evaluation
}

\newcommand{\artificialIntelligence}{
Natural Language Processing (NLP),
Deep Learning,
Computer Vision,
Recommendation Systems,
Chatbots,
Neural Networks,
Transfer Learning,
Model Optimization,
Hardware Acceleration
}

\newcommand{\researchSkills}{
AI Ethics,
Model Evaluation,
Experimentation
}

\newcommand{\specializedSkills}{
Algorithms,
Hardware Acceleration,
FPGA,
Verilog
}

% CORE COMPETENCIES
\newcommand{\problemSolving}{
Analytical thinking,
AI system design,
Model debugging,
Performance optimization
}

\newcommand{\leadership}{
Cross-functional collaboration,
Agile teamwork
}

\newcommand{\communication}{
Technical documentation,
AI explainability,
Knowledge transfer
}

\newcommand{\continuousLearning}{
Research papers,
Technology adoption,
Industry trends
}

% ============================================================
