% ============================================================
% RESUME CONTENT - OPTIMIZED FOR DATA ANALYST ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{Data Analyst} with hands-on experience in data analysis, visualization, and business intelligence. IBM certified with expertise in \textbf{Python}, \textbf{SQL}, \textbf{Pandas}, and data visualization tools. Proven ability to extract actionable insights from complex datasets, build interactive dashboards, and support data-driven decision making. Strong foundation in statistical analysis, data cleaning, and communicating findings to stakeholders.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Data Science Trainee}%
    {Digital Egypt Pioneers Initiative (DEPI)}%
    {Jun 2025 - Dec 2025}%
    {%
        \item Completed IBM Data Scientist certification with Python, SQL, and data analysis.
        \item Performed exploratory data analysis and feature engineering on real-world datasets.
        \item Delivered a capstone project with comprehensive data visualization and business insights.
    }%
    |||
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Present}%
    {%
        \item Developed complex SQL queries for database analysis and performance optimization.
        \item Collaborated with stakeholders to analyze business requirements and deliver data-driven solutions.
    }%
    |||
    {Resource Management Team Member}%
    {Enactus Cairo University}%
    {Dec 2025 - Present}%
    {%
        \item Engaged in survey design, market research, and data collection for problem validation.
        \item Analyzed research data to ensure solution relevance before project kickoff.
    }%
    |||%
}

% PROJECTS
\newcommand{\projectsList}{%
    {Jun 2025}%
    {https://github.com/KarimmYasser/music_store_analysis}%
    {Music Store Analysis}%
    {Conducted a comprehensive \textbf{data analysis} of music store sales using \textbf{Python} and \textbf{pandas}, performing \textbf{data cleaning}, integration, and generating key \textbf{business insights} with visualizations.}%
    |||
    {Nov 2025}%
    {https://github.com/KarimmYasser/Walmart-Sales-Forecasting-ML}%
    {Walmart Sales Forecasting Analysis}%
    {Analyzed sales data across 45 stores, performing \textbf{EDA}, \textbf{feature engineering} with 44 features, and built interactive \textbf{Streamlit} dashboards for business insights.}%
    |||
    {Sep 2025}%
    {https://github.com/KarimmYasser/heart_disease_prediction}%
    {Heart Disease Data Analysis}%
    {Performed comprehensive \textbf{data analysis} including preprocessing, statistical analysis, \textbf{feature selection}, and visualization via an interactive web dashboard.}%
    |||
    {Sep 2025}%
    {https://github.com/KarimmYasser/wuzzuf-job-scraper}%
    {Wuzzuf Jobs Data Scraper}%
    {Developed a \textbf{data collection} tool using Python and Selenium to extract job market data and export to structured CSV/JSON formats for analysis.}%
    |||
    {Mar 2025 – May 2025}%
    {https://github.com/KarimmYasser/sher-look}%
    {Sherlook Web Engine}%
    {Built a search engine processing 50K+ pages with custom \textbf{ranking algorithms} and data indexing.}%
    |||
    {Aug 2025 - Sep 2025}%
    {https://github.com/KarimmYasser/FollowersInstagram}%
    {Instagram Followers Analyzer}%
    {Developed a desktop application to \textbf{analyze} Instagram data exports and generate follower insights.}%
    |||%
}

% TECHNICAL SKILLS
\newcommand{\programmingLanguages}{
Python,
SQL,
R
}

\newcommand{\mobileDevelopment}{}

\newcommand{\frameworksLibraries}{
Pandas,
NumPy,
Matplotlib,
Seaborn,
Plotly,
Streamlit,
Selenium
}

\newcommand{\backendDatabase}{
MySQL,
SQLite,
PostgreSQL,
Query Optimization,
Database Design
}

\newcommand{\developmentTools}{
Jupyter Notebooks,
Excel,
Git,
GitHub,
VS Code,
Web Scraping
}

\newcommand{\softwareEngineering}{
ETL Processes,
Data Modeling,
Report Generation
}

\newcommand{\dataScience}{
Exploratory Data Analysis (EDA),
Data Cleaning,
Data Visualization,
Statistical Analysis,
Data Wrangling,
Business Intelligence,
KPI Tracking
}

\newcommand{\artificialIntelligence}{
Descriptive Statistics,
Inferential Statistics,
Regression Analysis,
Trend Analysis
}

\newcommand{\researchSkills}{
Survey Design,
Market Research,
Data Collection,
Problem Validation,
Report Writing
}

\newcommand{\specializedSkills}{}

% CORE COMPETENCIES
\newcommand{\problemSolving}{
Analytical thinking,
Statistical reasoning,
Problem decomposition,
Root cause identification
}

\newcommand{\leadership}{
Cross-functional collaboration,
Stakeholder management,
Agile teamwork
}

\newcommand{\communication}{
Data storytelling,
Dashboard creation,
Stakeholder presentations,
Technical documentation
}

\newcommand{\continuousLearning}{
Technology adoption,
Industry best practices,
Rapid skill acquisition
}

% ============================================================
