% ============================================================
% RESUME CONTENT - OPTIMIZED FOR ANDROID DEVELOPER ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{Android Developer} with hands-on experience building native Android applications using \textbf{Kotlin}, \textbf{Jetpack Compose}, and modern Android architecture patterns. Proven expertise in \textbf{MVVM/Clean Architecture}, dependency injection (Hilt/Dagger), Room database, and RESTful API integration. Strong foundation in mobile development with additional cross-platform experience in Flutter. Passionate about creating performant, user-friendly mobile applications with clean, maintainable code.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Android Developer Intern}%
    {Banque Misr}%
    {Jul 2025 - Sep 2025}%
    {%
        \item Developed native Android applications using Kotlin, Android Jetpack components, and Room Database for local data persistence.
        \item Implemented MVVM architecture patterns to create scalable and maintainable mobile solutions with enhanced user experience and optimized performance.
    }%
    |||
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Present}%
    {%
        \item Won first place in a 30+ team hackathon, earning a full-time position offer.
        \item Collaborated with back-end engineers and QA testers in an agile environment, implementing offline functionality and state management.
        \item Developed complex queries for offline database, gaining hands-on experience in database management and performance tuning.
    }%
    |||
    {Mobile Development Intern (Flutter \& ML)}%
    {Informatique}%
    {Jul 2025 - Aug 2025}%
    {%
        \item Integrated ML models into mobile apps using TFLite/ML Kit for on-device data processing.
    }%
    |||
    {Data Science Trainee}%
    {Digital Egypt Pioneers Initiative (DEPI)}%
    {Jun 2025 - Dec 2025}%
    {%
        \item Completed IBM Data Scientist certification; delivered capstone project with end-to-end ML pipeline.
    }%
    |||
    {Flutter Instructor}%
    {IEEE Cairo University SB}%
    {Feb 2025 - May 2025}%
    {%
        \item Instructed 30+ students in mobile development, state management, and API integration with 90\% satisfaction.
    }%
    |||
    {Mobile App Development Trainee}%
    {Orange Digital Center}%
    {Jan 2025 - Mar 2025}%
    {%
        \item Completed 96-hour mobile development training mastering cross-platform development and state management.
    }%
    |||
    {Flutter Developer Intern}%
    {SlashHub}%
    {Oct 2024 - Jan 2025}%
    {%
        \item Designed reactive UI components for AI-powered e-commerce chatbot, achieving 25\% improvement in user engagement.
    }%
    |||%
}

% PROJECTS
\newcommand{\projectsList}{%
    {Aug 2025 - Sep 2025}%
    {https://github.com/KarimmYasser/coffee_shop}%
    {Coffee Shop Android App}%
    {Developed an offline-first coffee shop app using \textbf{Kotlin Jetpack Compose}, implementing \textbf{Clean Architecture} with \textbf{MVVM}, \textbf{Hilt} for dependency injection, \textbf{Room} for local persistence, and \textbf{Retrofit} for API integration.}%
    |||
    {Aug 2025}%
    {https://github.com/KarimmYasser/recipe-box}%
    {RecipeBox Recipe Management App}%
    {Developed a modern, offline-first Android recipe app using \textbf{Jetpack Compose}, architected with \textbf{Clean Architecture (MVVM)}, \textbf{Room} database, and \textbf{Dagger/Hilt} for dependency injection.}%
    |||
    {Jul 2025 - Aug 2025}%
    {https://github.com/KarimmYasser/fakestore-ecommerce-app}%
    {FakeStore E-Commerce App}%
    {Built a modern Android e-commerce app in \textbf{Kotlin}, demonstrating \textbf{Jetpack Compose} for UI, \textbf{Paging 3} for efficient data loading, and \textbf{Room} for local cart persistence.}%
    |||
    {Jul 2025}%
    {https://github.com/KarimmYasser/secure-notes}%
    {SecureNotes Android App}%
    {Developed a secure Android notes application using \textbf{Jetpack Compose} for the UI and \textbf{Proto DataStore} for type-safe, persistent settings management.}%
    |||
    {Jul 2025}%
    {https://github.com/KarimmYasser/personal-finance-tracker}%
    {Personal Finance Tracker}%
    {Collaborated to develop an Android app for logging expenses, implementing \textbf{Activity lifecycle}, \textbf{Intents}, and \textbf{SharedPreferences}.}%
    |||
    {Jun 2025}%
    {https://github.com/KarimmYasser/isupply_app}%
    {i'Supply POS App - First Place Hackathon Winner}%
    {Developed a cross-platform POS system for desktop and mobile with \textbf{offline synchronization}, \textbf{Hive} local storage, and \textbf{Supabase} backend.}%
    |||
    {Oct 2025 - Dec 2025}%
    {https://github.com/KarimmYasser/yapper-mobile}%
    {Yapper - X Clone Mobile App}%
    {Built a cross-platform \textbf{React Native} social media app with real-time \textbf{WebSocket} messaging, push notifications, and \textbf{CI/CD} automation.}%
    |||
    {Feb 2025 - Mar 2025}%
    {https://github.com/KarimmYasser/hangouts_crincale}%
    {Hangouts Crincale – Audio Analysis Tool}%
    {Engineered a cross-platform audio analysis application in \textbf{Flutter} with frequency response visualization and hardware control.}%
    |||
    {Nov 2025}%
    {https://github.com/KarimmYasser/Walmart-Sales-Forecasting-ML}%
    {Walmart Sales Forecasting - ML Pipeline}%
    {Developed an end-to-end ML pipeline achieving \textbf{99.96\% R²} accuracy, deployed via \textbf{FastAPI} and \textbf{Streamlit} with \textbf{Docker}.}%
    |||%
}

% TECHNICAL SKILLS
\newcommand{\programmingLanguages}{
Kotlin,
Java,
Dart,
SQL,
Python
}

\newcommand{\mobileDevelopment}{
Android Development (Kotlin, Jetpack Compose, XML Views),
Flutter (Mobile \& Desktop),
Cross-platform Development
}

\newcommand{\frameworksLibraries}{
Dagger/Hilt,
Android Navigation Component,
Room,
Retrofit,
Coroutines/Flow,
Paging 3,
DataStore,
WorkManager,
Firebase,
RESTful APIs,
Flutter Bloc,
Provider
}

\newcommand{\backendDatabase}{
Room,
SQLite,
Firebase,
Supabase,
Offline-first Architecture,
API Integration
}

\newcommand{\developmentTools}{
Android Studio,
Git,
GitHub,
Gradle,
Postman,
Figma,
Agile/Scrum
}

\newcommand{\softwareEngineering}{
Clean Architecture,
MVVM,
SOLID Principles,
Dependency Injection,
State Management,
Object-Oriented Programming (OOP),
Design Patterns
}

\newcommand{\dataScience}{
Data Structures,
Algorithms
}

\newcommand{\artificialIntelligence}{
ML Integration (TFLite/ML Kit)
}

\newcommand{\researchSkills}{
Technical Documentation,
Code Review
}

\newcommand{\specializedSkills}{
Algorithms,
Data Structures,
ML Integration (TFLite/ML Kit)
}

% CORE COMPETENCIES
\newcommand{\problemSolving}{
Analytical thinking,
Problem decomposition,
Debugging,
Root cause identification
}

\newcommand{\leadership}{
Technical mentoring,
Code review,
Cross-functional collaboration,
Agile teamwork
}

\newcommand{\communication}{
Technical documentation,
Knowledge transfer,
Remote collaboration
}

\newcommand{\continuousLearning}{
Technology adoption,
Industry best practices,
Rapid skill acquisition
}

% ============================================================
