% ============================================================
% RESUME CONTENT - OPTIMIZED FOR C++ DEVELOPER ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{C++ Developer} with strong foundation in object-oriented programming, data structures, and algorithms. Experienced in building desktop applications using Qt framework and implementing game development projects. Proficient in memory management, performance optimization, and systems programming. Background in low-level development with hardware description languages and embedded systems concepts. Strong problem-solving skills with experience in competitive programming principles.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Present}%
    {%
        \item Won first place in a 30+ team hackathon, earning a full-time position offer.
        \item Developed scalable software solutions with focus on performance and code quality.
        \item Collaborated in agile environment applying software engineering best practices.
    }%
    |||
    {Android Developer Intern}%
    {Banque Misr}%
    {Jul 2025 - Aug 2025}%
    {%
        \item Developed native applications using OOP principles and design patterns.
        \item Implemented Clean Architecture (MVVM) ensuring maintainable, testable code.
    }%
    |||
    {Data Science Trainee}%
    {Digital Egypt Pioneers Initiative (DEPI)}%
    {Jun 2025 - Dec 2025}%
    {%
        \item Applied algorithms and data structures for efficient data processing pipelines.
    }%
    |||%
}

% PROJECTS
\newcommand{\projectsList}{%
    {Feb 2024 – Apr 2024}%
    {https://github.com/KarimmYasser/Alien_Invasion_Project}%
    {Alien Invasion - C++ Game}%
    {Developed a complete game in \textbf{C++} with OOP principles, \textbf{linked lists}, \textbf{queues}, and \textbf{stacks} for entity management.}%
    |||
    {Nov 2023 - Jan 2024}%
    {https://github.com/KarimmYasser/paint-for-kids}%
    {Paint for Kids - C++ Desktop Application}%
    {Built a Qt-based drawing application implementing \textbf{polymorphism}, \textbf{inheritance}, and \textbf{design patterns}.}%
    |||
    {Feb 2025}%
    {https://github.com/KarimmYasser/cmpsh}%
    {Unix Shell Implementation}%
    {Implemented a shell in \textbf{C} with process management, pipes, I/O redirection, and signal handling.}%
    |||
    {Nov 2025 - Dec 2025}%
    {https://github.com/KarimmYasser/VLSI-Convolution-Systolic-Accelerator}%
    {VLSI Convolution Accelerator}%
    {Designed a hardware accelerator in \textbf{Verilog} applying \textbf{C++-like algorithmic thinking} for systolic arrays.}%
    |||
    {Mar 2024 - May 2024}%
    {https://github.com/KarimmYasser/stall_3alda2ery}%
    {5-Stage Pipelined Processor}%
    {Designed a MIPS processor implementing \textbf{pipeline architecture} and \textbf{hazard handling} in Verilog.}%
    |||
    {Mar 2025 – May 2025}%
    {https://github.com/KarimmYasser/sher-look}%
    {Sherlook Search Engine}%
    {Implemented search algorithms with \textbf{efficient data structures} processing 50K+ pages.}%
    |||
    {Mar 2025 – May 2025}%
    {https://github.com/KarimmYasser/kernel-sim-ohh-s}%
    {Operating System Scheduler}%
    {Developed an OS scheduler in \textbf{C} implementing \textbf{process scheduling algorithms} and memory management.}%
    |||%
}

% TECHNICAL SKILLS
\newcommand{\programmingLanguages}{
\textbf{C++},
C,
Python,
Java,
Dart
}

\newcommand{\mobileDevelopment}{
Qt Framework,
Desktop Applications,
Cross-platform Development
}

\newcommand{\frameworksLibraries}{
STL,
Qt,
OpenGL,
CMake,
Make
}

\newcommand{\backendDatabase}{
PostgreSQL,
MySQL,
SQLite,
Data Structures
}

\newcommand{\developmentTools}{
Git,
GitHub,
VS Code,
Visual Studio,
GDB,
Valgrind,
CMake
}

\newcommand{\softwareEngineering}{
Object-Oriented Programming (OOP),
Design Patterns,
SOLID Principles,
Clean Architecture,
Memory Management,
Performance Optimization
}

\newcommand{\dataScience}{
Algorithms,
Data Structures,
Complexity Analysis
}

\newcommand{\artificialIntelligence}{
Algorithm Optimization,
Graph Algorithms
}

\newcommand{\researchSkills}{
Technical Documentation,
Code Review,
Best Practices
}

\newcommand{\specializedSkills}{
Systems Programming,
Embedded Systems,
Verilog,
FPGA,
Hardware-Software Interface,
Low-level Debugging
}

% CORE COMPETENCIES
\newcommand{\problemSolving}{
Algorithm design,
Data structure optimization,
Debugging,
Performance profiling
}

\newcommand{\leadership}{
Code review,
Team collaboration,
Mentoring
}

\newcommand{\communication}{
Technical documentation,
Code readability,
Knowledge sharing
}

\newcommand{\continuousLearning}{
Modern C++ standards,
Best practices,
System design
}

% ============================================================
