% ============================================================
% RESUME CONTENT - OPTIMIZED FOR SYSTEM DEVELOPER ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{Systems Developer} with a deep understanding of low-level programming, operating systems, and computer architecture. Proficient in \textbf{C/C++}, \textbf{Rust}, and Assembly language. Experienced in building high-performance game engines, custom UNIX shells, OS schedulers, and robust bare-metal embedded firmware. Strong background in memory management, process synchronization, concurrent programming, and performance optimization for mission-critical systems.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Dec 2025}%
    {%
        \item Won first place in a 30+ team hackathon, earning a full-time position offer.
        \item Developed scalable software architectures and optimized complex database queries for a production system handling thousands of concurrent interactions.
    }%
    |||
    {Session Lead}%
    {Udacity (Digital Egypt Cubs Initiative - DECI)}%
    {Nov 2025 - Mar 2026}%
    {%
        \item Led weekly sessions delivering core computer fundamentals, focusing on system architecture, operating systems, and low-level data structures.
    }%
    |||
    {Resource Management Team Member}%
    {Enactus Cairo University}%
    {Dec 2025 - Feb 2026}%
    {%
        \item Ensured optimal resource allocation and system efficiency planning for complex engineering projects.
    }%
    |||%
}

% PROJECTS
\newcommand{\projectsList}{%
    {Jun 2026}%
    {https://github.com/KarimmYasser/GSoCPathfinder}%
    {GSoC Pathfinder - High Performance Matcher}%
    {Engineered a \textbf{high-performance Rust scoring engine} compiled with \textbf{Maturin \& PyO3} bindings to offload heavy mathematical calculations for an AI matching system. Implemented a \textbf{7-Factor weighted ranking} algorithm including CV-frequency-weighted Jaccard similarity. Integrated with \textbf{FastAPI}, \textbf{Neo4j}, and \textbf{Qdrant} to canonicalize and process 11 years of historical data.}%
    |||
    {Mar 2026 - May 2026}%
    {https://github.com/KarimmYasser/aladdin-nasiras-revenge}%
    {Aladdin: Nasira's Revenge - C++ Game Engine}%
    {Developed a high-performance 3D engine using \textbf{C++17} featuring a data-driven \textbf{Entity Component System (ECS)} with deferred lifecycle management for strict memory stability. Engineered a highly optimized command-based renderer.}%
    |||
    {Apr 2026 - May 2026}%
    {https://github.com/KarimmYasser/robot-wall-follower}%
    {Autonomous Wall-Following Robot Firmware}%
    {Developed professional-grade \textbf{bare-metal C firmware} for the ATmega328P utilizing Timer1 and EXTI/PCINT interrupts for non-blocking sensing. Implemented a robust \textbf{Finite State Machine (FSM)} for predictable autonomous decision-making.}%
    |||
    {Feb 2026 - Mar 2026}%
    {https://github.com/KarimmYasser/rusty-sherlook-engine}%
    {Rusty Sherlook - High-Performance Search Engine}%
    {Engineered a high-concurrency extension to the Sherlook search engine in \textbf{Rust} utilizing \textbf{Tokio}. Integrated \textbf{Qdrant} for semantic vector search and \textbf{Neo4j} for advanced graph-based PageRank processing.}%
    |||
    {Feb 2025}%
    {https://github.com/KarimmYasser/cmpsh}%
    {Custom Unix Shell (cmpsh)}%
    {Implemented a lightweight Unix shell in \textbf{C}, demonstrating core OS concepts like system calls, process management (fork/exec), IPC (piping), and I/O redirection.}%
    |||
    {Mar 2025 - May 2025}%
    {https://github.com/KarimmYasser/kernel-sim-ohh-s}%
    {OS Process Scheduler Simulator}%
    {Simulated multiple CPU scheduling algorithms (FCFS, SJF, Priority, Round Robin) in \textbf{C} with real-time visualization and complex process synchronization metric tracking.}%
    |||
    {Oct 2025 - Dec 2025}%
    {https://github.com/KarimmYasser/stall_3alda2ery}%
    {5-Stage Pipelined Processor}%
    {Designed a 32-bit 5-stage pipelined MIPS processor in \textbf{VHDL} with Von Neumann architecture, fully supporting hardware interrupts and mapped I/O. Implemented hazard handling via data forwarding.}%
    |||
    {Nov 2025 - Dec 2025}%
    {https://github.com/KarimmYasser/VLSI-Convolution-Systolic-Accelerator}%
    {VLSI Convolution Systolic Accelerator}%
    {Designed a high-performance 2D convolution accelerator in \textbf{Verilog} using an 8x8 systolic array targeting the \textbf{SKY130 PDK}. Successfully executed the complete \textbf{RTL-to-GDSII} flow via \textbf{OpenLane}.}%
    |||
    {Apr 2026}%
    {https://github.com/KarimmYasser/hash-clash-keys-please}%
    {Multi-Architecture Hash Optimization}%
    {Engineered a high-performance BLAKE-256 implementation in \textbf{C}, utilizing low-level bitwise operations and loop unrolling to maximize CPU throughput.}%
    |||%
}

% TECHNICAL SKILLS
\newcommand{\programmingLanguages}{C, C++, Rust, Assembly (MIPS, AVR), Python, VHDL, Verilog}
\newcommand{\mobileDevelopment}{}
\newcommand{\frameworksLibraries}{POSIX API, OpenGL, Rayon, PyO3}
\newcommand{\backendDatabase}{}
\newcommand{\developmentTools}{GDB, Valgrind, Make, CMake, Git, Linux/Unix, Bash}
\newcommand{\softwareEngineering}{Memory Management, Process IPC, Multithreading, Concurrency, Hardware-Software Interface}
\newcommand{\dataScience}{}
\newcommand{\artificialIntelligence}{}
\newcommand{\researchSkills}{}
\newcommand{\specializedSkills}{Operating Systems, Embedded C (Bare-Metal, Register-Level), Computer Architecture, Microprocessors}

% CORE COMPETENCIES
\newcommand{\problemSolving}{Memory leak debugging, Concurrency issue resolution, System-level bottleneck optimization}
\newcommand{\leadership}{Technical code review, Low-level architecture planning}
\newcommand{\communication}{System documentation, Low-level concept explanation}
\newcommand{\continuousLearning}{Modern C++ adoption, Rust systems programming, Advanced OS design}
% ============================================================

