% ============================================================
% RESUME CONTENT - OPTIMIZED FOR ML ENGINEER ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{Machine Learning Engineer} with hands-on experience building, optimizing, and deploying end-to-end ML pipelines and agentic AI systems. IBM certified in Data Science with proven expertise in \textbf{Python}, \textbf{PyTorch}, \textbf{Scikit-Learn}, and \textbf{MLOps} workflows. Specializes in deep learning models, anomaly detection, NLP, and model optimization. Demonstrated ability to accelerate inference speeds, integrate on-device AI, and deploy scalable cloud solutions via \textbf{FastAPI} and \textbf{Docker}.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Data Science Trainee}%
    {Digital Egypt Pioneers Initiative (DEPI)}%
    {Jun 2025 - Dec 2025}%
    {%
        \item Completed IBM Data Scientist certification covering Python, SQL, and advanced machine learning model families.
        \item Implemented MLOps workflows using MLflow and HuggingFace for model versioning, experiment tracking, and deployment.
        \item Delivered a capstone project applying an end-to-end ML pipeline with extensive feature engineering and hyperparameter tuning.
    }%
    |||
    {Agentic AI Trainee}%
    {Orange Digital Center Egypt}%
    {Feb 2026 - Apr 2026}%
    {%
        \item Built autonomous AI agents using LangChain/LangGraph, implementing memory management and multi-agent collaboration pipelines.
        \item Designed self-healing agent loops with hallucination detection guards and evaluated local vs. remote LLMs for cost and latency optimization.
    }%
    |||
    {Mobile Development Intern (Flutter \& ML)}%
    {Informatique}%
    {Jul 2025 - Aug 2025}%
    {%
        \item Integrated Machine Learning models into mobile applications utilizing TFLite and ML Kit for optimized on-device inference.
        \item Developed cross-platform features bridging application logic with ML frameworks for real-time data processing.
    }%
    |||
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Dec 2025}%
    {%
        \item Developed complex queries and optimized data pipelines for a production database handling robust data transformations.
    }%
    |||%
}

% PROJECTS
\newcommand{\projectsList}{%
    {Jun 2026}%
    {https://github.com/KarimmYasser/GSoCPathfinder}%
    {GSoC Pathfinder - AI Agent Organization Matcher}%
    {Architected an end-to-end \textbf{AI Agent} system matching candidate CVs to GSoC organizations via a \textbf{LangGraph} pipeline. Engineered a \textbf{Rust scoring engine} to execute a \textbf{7-Factor ranking} algorithm using CV-frequency-weighted Jaccard similarity. Canonicalized 11 years of data into a \textbf{Neo4j} + \textbf{Qdrant} dual-database store for semantic vector search and graph retrieval.}%
    |||
    {Mar 2026 - May 2026}%
    {https://github.com/KarimmYasser/machine-sound-classification}%
    {Industrial Machine Sound Classification \& Anomaly Detection}%
    {Architected a Dual-Track AI pipeline achieving \textbf{95.61\% accuracy} using an \textbf{XGBoost} edge champion and \textbf{EfficientAT} cloud model. Engineered a \textbf{Rust} extraction engine achieving a \textbf{57x speedup} and resolved severe data imbalance using \textbf{CGANs}.}%
    |||
    {Feb 2026}%
    {https://github.com/KarimmYasser/braTs-ai-hackathon-ODCxINSTANT}%
    {BioMedIAMBZ - Brain Tumor Segmentation (1st Place)}%
    {Won \textbf{1st place} in an AI Hackathon by developing a 3D brain tumor segmentation pipeline using \textbf{MedNeXt} with \textbf{PyTorch} and \textbf{MONAI}. Deployed the model via a \textbf{FastAPI} backend for real-time clinical inference.}%
    |||
    {Nov 2025}%
    {https://github.com/KarimmYasser/Walmart-Sales-Forecasting-ML}%
    {Walmart Sales Forecasting - ML Pipeline}%
    {Developed an end-to-end ML pipeline across 45 stores achieving \textbf{99.96\% R²} with Random Forest. Engineered 44 robust features and deployed the system via \textbf{FastAPI}, \textbf{Docker}, and \textbf{MLflow}.}%
    |||
    {Mar 2026 - Apr 2026}%
    {https://github.com/KarimmYasser/ai-eval-framework}%
    {AI API Evaluation Framework}%
    {Engineered an evaluation platform for Multimodal AI and Agentic Workflows with a \textbf{Dual-Metric Framework} to analyze model fidelity. Developed an \textbf{Agent Trace Viewer} for granular credit assignment.}%
    |||
    {Nov 2024 - Dec 2024}%
    {https://github.com/KarimmYasser/Slash-Fashion-Assistant-App}%
    {Fashion Assistant - AI-Powered Chatbot}%
    {Built a personalized shopping assistant with an \textbf{NLP-powered chatbot} and intelligent \textbf{product recommendation system}, demonstrating strong capabilities in conversational AI integration.}%
    |||%
}

% TECHNICAL SKILLS
\newcommand{\programmingLanguages}{Python, SQL, R, C++, Rust, JavaScript}
\newcommand{\mobileDevelopment}{}
\newcommand{\frameworksLibraries}{PyTorch, Scikit-learn, MLflow, Hugging Face, Transformers, MONAI, Pandas, NumPy, FastAPI, LangChain}
\newcommand{\backendDatabase}{}
\newcommand{\developmentTools}{}
\newcommand{\softwareEngineering}{MLOps, Clean Architecture, Model Deployment, Microservices}
\newcommand{\dataScience}{Data Preprocessing, Feature Engineering, EDA, Model Evaluation}
\newcommand{\artificialIntelligence}{Deep Learning, Agentic AI, NLP, Time Series Forecasting, Computer Vision, GANs}
\newcommand{\researchSkills}{}
\newcommand{\specializedSkills}{}

% CORE COMPETENCIES
\newcommand{\problemSolving}{Analytical thinking, Model debugging, Performance tuning, Root cause identification}
\newcommand{\leadership}{Technical collaboration, Hackathon Leadership, Cross-functional communication}
\newcommand{\communication}{Data storytelling, Technical documentation, Stakeholder presentations}
\newcommand{\continuousLearning}{Adopting SOTA models, Reading research papers, Rapid prototyping}
% ============================================================

