% ============================================================
% RESUME CONTENT - OPTIMIZED FOR MOBILE DEVELOPER ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{Mobile App Developer} with 2+ years of experience building native and cross-platform mobile applications. Proficient in \textbf{Flutter}, \textbf{Android (Kotlin/Jetpack Compose)}, and \textbf{React Native}. Strong expertise in clean architecture, state management, offline-first development, and RESTful API integration. Proven track record delivering production apps with Firebase, Supabase, and ML integration. Experience teaching mobile development and leading agile teams.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Present}%
    {%
        \item Won first place in a 30+ team hackathon, earning a full-time position offer.
        \item Collaborated with back-end engineers and QA testers in an agile environment, analyzing the Flutter desktop app's architecture and state management.
        \item Implemented offline functionality and developed complex queries for offline database with performance optimization.
    }%
    |||
    {Android Developer Intern}%
    {Banque Misr}%
    {Jul 2025 - Sep 2025}%
    {%
        \item Developed native Android applications using Kotlin, Android Jetpack components, and Room Database.
        \item Implemented MVVM architecture patterns to create scalable and maintainable mobile solutions.
    }%
    |||
    {Mobile Development Intern (Flutter \& ML)}%
    {Informatique}%
    {Jul 2025 - Aug 2025}%
    {%
        \item Integrated ML models into Flutter apps using TFLite/ML Kit for on-device data processing.
    }%
    |||
    {Data Science Trainee}%
    {Digital Egypt Pioneers Initiative (DEPI)}%
    {Jun 2025 - Dec 2025}%
    {%
        \item Completed IBM Data Scientist certification; delivered capstone project with end-to-end ML pipeline.
    }%
    |||
    {Flutter Instructor}%
    {IEEE Cairo University SB}%
    {Feb 2025 - May 2025}%
    {%
        \item Instructed 30+ students in Flutter development, state management, and API integration with 90\% satisfaction.
    }%
    |||
    {Mobile App Development Trainee}%
    {Orange Digital Center}%
    {Jan 2025 - Mar 2025}%
    {%
        \item Completed 96-hour Flutter training mastering cross-platform development and state management.
    }%
    |||
    {Flutter Developer Intern}%
    {SlashHub}%
    {Oct 2024 - Jan 2025}%
    {%
        \item Designed reactive UI components for AI-powered e-commerce chatbot, achieving 25\% improvement in user engagement.
    }%
    |||%
}

% PROJECTS
\newcommand{\projectsList}{%
    {Jun 2025}%
    {https://github.com/KarimmYasser/isupply_app}%
    {i'Supply POS App - First Place Hackathon Winner}%
    {Developed a cross-platform \textbf{Flutter POS system} for desktop and mobile, featuring inventory search, cart management, checkout, and invoice tracking. Integrated \textbf{Hive} for local storage and \textbf{Supabase} for the back-end with offline synchronization.}%
    |||
    {Aug 2025 - Sep 2025}%
    {https://github.com/KarimmYasser/coffee_shop}%
    {Coffee Shop Android App}%
    {Developed an offline-first coffee shop app using \textbf{Kotlin Jetpack Compose}, implementing \textbf{Clean Architecture} with \textbf{MVVM}, \textbf{Hilt} for dependency injection, \textbf{Room}, and \textbf{Retrofit}.}%
    |||
    {Oct 2025 - Dec 2025}%
    {https://github.com/KarimmYasser/yapper-mobile}%
    {Yapper - X Clone Mobile App}%
    {Built a cross-platform \textbf{React Native} social media app with \textbf{Expo}, featuring real-time \textbf{WebSocket} messaging, push notifications, multi-language support with full \textbf{RTL}, and \textbf{CI/CD} automation via EAS.}%
    |||
    {Aug 2025}%
    {https://github.com/KarimmYasser/recipe-box}%
    {RecipeBox Recipe Management App}%
    {Developed an offline-first Android recipe app using \textbf{Jetpack Compose}, \textbf{Clean Architecture (MVVM)}, \textbf{Room}, and \textbf{Dagger/Hilt}.}%
    |||
    {Jul 2025 - Aug 2025}%
    {https://github.com/KarimmYasser/fakestore-ecommerce-app}%
    {FakeStore E-Commerce App}%
    {Built an Android e-commerce app in \textbf{Kotlin}, using \textbf{Jetpack Compose}, \textbf{Paging 3} for efficient data loading, and \textbf{Room} for local persistence.}%
    |||
    {Feb 2025 - Mar 2025}%
    {https://github.com/KarimmYasser/hangouts_crincale}%
    {Hangouts Crincale – Audio Analysis Tool}%
    {Engineered a cross-platform audio analysis application in \textbf{Flutter} with frequency response visualization and parametric equalization.}%
    |||
    {Jul 2025}%
    {https://github.com/KarimmYasser/secure-notes}%
    {SecureNotes Android App}%
    {Developed a secure Android notes app using \textbf{Jetpack Compose} and \textbf{Proto DataStore} for persistent settings.}%
    |||
    {Nov 2024 - Dec 2024}%
    {https://github.com/KarimmYasser/Slash-Fashion-Assistant-App}%
    {Fashion Assistant - E-commerce Platform}%
    {Built a \textbf{Flutter} personalized shopping assistant with AI-powered chatbot and product recommendations.}%
    |||
    {Jun 2024 - July 2024}%
    {https://github.com/KarimmYasser/Cooking-up-application}%
    {Cooking Up App}%
    {Developed a \textbf{Flutter}-based recipe app with offline access, category filters, and interactive cooking tools.}%
    |||
    {Mar 2025 - May 2025}%
    {https://github.com/KarimmYasser/zengbary-app}%
    {Zengbary App}%
    {Developed a \textbf{Flutter} app to remotely control a microprocessor-based robot with HTTP communication.}%
    |||%
}

% TECHNICAL SKILLS
\newcommand{\programmingLanguages}{
Dart,
Kotlin,
Java,
TypeScript,
SQL,
Python
}

\newcommand{\mobileDevelopment}{
Flutter (Mobile \& Desktop),
Android Development (Kotlin, Jetpack Compose, XML Views),
React Native (Expo),
Cross-platform Development
}

\newcommand{\frameworksLibraries}{
Flutter Bloc,
Riverpod,
Provider,
GetX,
Dagger/Hilt,
Android Navigation Component,
Room,
Retrofit,
Paging 3,
Coroutines/Flow,
DataStore,
Firebase,
RESTful APIs,
Zustand,
React Query,
Socket.io
}

\newcommand{\backendDatabase}{
Firebase,
Supabase,
Room,
SQLite,
Hive,
Offline-first Architecture,
API Integration
}

\newcommand{\developmentTools}{
Android Studio,
VS Code,
Git,
GitHub,
Gradle,
Postman,
Figma,
EAS (Expo),
Agile/Scrum
}

\newcommand{\softwareEngineering}{
Clean Architecture,
MVVM,
SOLID Principles,
Dependency Injection,
State Management,
Object-Oriented Programming (OOP),
Design Patterns
}

\newcommand{\dataScience}{
Data Structures,
Algorithms
}

\newcommand{\artificialIntelligence}{
ML Integration (TFLite/ML Kit)
}

\newcommand{\researchSkills}{
Technical Documentation,
Code Review
}

\newcommand{\specializedSkills}{
Algorithms,
Data Structures,
ML Integration (TFLite/ML Kit)
}

% CORE COMPETENCIES
\newcommand{\problemSolving}{
Analytical thinking,
Problem decomposition,
Debugging,
Root cause identification
}

\newcommand{\leadership}{
Technical mentoring,
Code review,
Cross-functional collaboration,
Agile teamwork
}

\newcommand{\communication}{
Technical documentation,
Knowledge transfer,
Remote collaboration
}

\newcommand{\continuousLearning}{
Technology adoption,
Industry best practices,
Rapid skill acquisition
}

% ============================================================
