% ============================================================
% RESUME CONTENT - OPTIMIZED FOR PROGRAMMING INSTRUCTOR ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{Programming Instructor} with proven teaching experience and hands-on industry expertise. Former Flutter Instructor at IEEE CU and Session Lead at Udacity with track record of simplifying complex concepts for diverse audiences. Strong foundation across multiple domains including mobile development, data science, systems programming, and hardware design. Excellent communication skills with experience creating curricula, mentoring students, and leading technical sessions. Passionate about knowledge sharing and building the next generation of developers.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Flutter Instructor}%
    {IEEE CU}%
    {Jun 2024 - Aug 2024}%
    {%
        \item Delivered comprehensive Flutter course curriculum covering Dart fundamentals to advanced concepts.
        \item Created hands-on projects and assignments enabling practical skill development for students.
        \item Mentored students through complex mobile development concepts with clear explanations.
    }%
    |||
    {Session Lead}%
    {Udacity}%
    {Nov 2023 - Aug 2024}%
    {%
        \item Led technical mentoring sessions helping students master programming concepts.
        \item Provided personalized guidance and code review to support student success.
        \item Developed effective teaching strategies for diverse learning styles.
    }%
    |||
    {Data Science Trainee}%
    {Digital Egypt Pioneers Initiative (DEPI)}%
    {Jun 2025 - Dec 2025}%
    {%
        \item Completed IBM Data Scientist certification with Python and machine learning.
        \item Gained teaching-relevant expertise in Python, SQL, and data analysis.
    }%
    |||
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Present}%
    {%
        \item Won first place in a 30+ team hackathon demonstrating technical excellence.
        \item Industry experience providing real-world context for teaching.
    }%
    |||
    {Flutter Developer Intern}%
    {SlashHub}%
    {Oct 2024 - Jan 2025}%
    {%
        \item Developed practical mobile development skills applicable to curriculum design.
    }%
    |||
    {Mobile Development Intern}%
    {Informatique}%
    {Jul 2025 - Aug 2025}%
    {%
        \item Gained ML integration experience for advanced curriculum topics.
    }%
    |||
    {Flutter Developer Intern}%
    {Orange Digital Center}%
    {Jul 2024 - Aug 2024}%
    {%
        \item Built real-world application skills for practical teaching examples.
    }%
    |||%
}

% PROJECTS - Diverse portfolio demonstrating broad teaching capability
\newcommand{\projectsList}{%
    {Nov 2024 - Dec 2024}%
    {https://github.com/KarimmYasser/Slash-Fashion-Assistant-App}%
    {Fashion Assistant App - Mobile Development}%
    {Built a complete Flutter app demonstrating \textbf{state management}, \textbf{API integration}, and \textbf{clean architecture} - ideal teaching example.}%
    |||
    {Nov 2025}%
    {https://github.com/KarimmYasser/Walmart-Sales-Forecasting-ML}%
    {Walmart ML Pipeline - Data Science}%
    {End-to-end ML project demonstrating \textbf{Python}, \textbf{data analysis}, and \textbf{model deployment} for data science curriculum.}%
    |||
    {Feb 2024 – Apr 2024}%
    {https://github.com/KarimmYasser/Alien_Invasion_Project}%
    {Alien Invasion Game - C++ Fundamentals}%
    {Comprehensive OOP project teaching \textbf{data structures}, \textbf{inheritance}, and \textbf{polymorphism} concepts.}%
    |||
    {Feb 2025}%
    {https://github.com/KarimmYasser/cmpsh}%
    {Unix Shell - Systems Programming}%
    {Educational project demonstrating \textbf{process management}, \textbf{system calls}, and \textbf{C programming}.}%
    |||
    {Mar 2024 - May 2024}%
    {https://github.com/KarimmYasser/stall_3alda2ery}%
    {MIPS Processor - Computer Architecture}%
    {Comprehensive Verilog project teaching \textbf{processor design} and \textbf{pipeline architecture}.}%
    |||
    {Mar 2025 – May 2025}%
    {https://github.com/KarimmYasser/sher-look}%
    {Sherlook Search Engine}%
    {Full-stack project demonstrating \textbf{algorithms}, \textbf{web development}, and \textbf{database design}.}%
    |||%
}

% TECHNICAL SKILLS - Broad expertise for diverse teaching
\newcommand{\programmingLanguages}{
\textbf{Dart},
\textbf{Python},
\textbf{C++},
C,
Java,
JavaScript,
SQL
}

\newcommand{\mobileDevelopment}{
\textbf{Flutter},
Android Development,
React Native,
Mobile Architecture
}

\newcommand{\frameworksLibraries}{
Bloc/Cubit,
Provider,
Scikit-learn,
TensorFlow,
FastAPI,
Qt
}

\newcommand{\backendDatabase}{
Firebase,
PostgreSQL,
MySQL,
REST APIs
}

\newcommand{\developmentTools}{
Git,
GitHub,
VS Code,
Android Studio,
Docker,
Jupyter Notebooks
}

\newcommand{\softwareEngineering}{
Clean Architecture,
Design Patterns,
OOP Principles,
SOLID,
Agile Methodology
}

\newcommand{\dataScience}{
Data Analysis,
Machine Learning,
Data Visualization
}

\newcommand{\artificialIntelligence}{
ML Fundamentals,
Model Training,
Feature Engineering
}

\newcommand{\researchSkills}{
\textbf{Curriculum Design},
\textbf{Technical Writing},
\textbf{Documentation}
}

\newcommand{\specializedSkills}{
\textbf{Teaching},
\textbf{Mentoring},
\textbf{Public Speaking},
Computer Architecture,
Systems Programming,
Verilog
}

% CORE COMPETENCIES
\newcommand{\problemSolving}{
Breaking down complex concepts,
Creating learning paths,
Identifying knowledge gaps
}

\newcommand{\leadership}{
\textbf{Mentoring students},
\textbf{Leading sessions},
Team collaboration,
Curriculum development
}

\newcommand{\communication}{
\textbf{Clear explanations},
\textbf{Technical presentation},
Active listening,
Feedback delivery
}

\newcommand{\continuousLearning}{
Industry trends,
New technologies,
Teaching methodologies
}

% ============================================================
