% ============================================================
% RESUME CONTENT - OPTIMIZED FOR AGENTIC AI ROLES
% ============================================================
% Target: Agentic AI Engineer / AI Agent Developer roles
% Key Focus: LLM-powered agents, tool use, multi-agent systems,
%            RAG, knowledge graphs, autonomous workflows, LangChain/LangGraph
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY - Tailored for Agentic AI roles
\newcommand{\mySummary}{%
\textbf{Agentic AI Engineer} with hands-on experience designing and deploying \textbf{LLM-powered autonomous agents} using \textbf{LangChain}, \textbf{LangGraph}, and \textbf{Neo4j} knowledge graphs. Built production-grade agents with self-healing error recovery, tool orchestration, structured output generation, and multi-turn conversational memory. IBM-certified in Data Science with strong foundations in \textbf{Python}, \textbf{MLOps}, and \textbf{end-to-end ML pipelines}. Experience integrating AI into mobile and web applications, evaluating local vs. remote LLMs for cost optimization, and shipping AI-driven features that improved user engagement by 25\%.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% ============================================================
% WORK EXPERIENCE - Prioritized for agentic AI relevance
% ============================================================
\newcommand{\experienceList}{%
    {Agentic AI Trainee}%
    {Orange Digital Center Egypt}%
    {Feb 2026 - Apr 2026}%
    {%
        \item Built \textbf{autonomous AI agents} using \textbf{LLMs} and the \textbf{LangChain/LangGraph} ecosystem, implementing memory management, context windows, and multi-turn conversation handling.
        \item Engineered \textbf{multi-agent collaboration} pipelines with tool orchestration, API-based automation, and knowledge integration via \textbf{Neo4j} and \textbf{SQLite}.
        \item Designed \textbf{self-healing agent loops} with hallucination detection guards and autonomous error recovery for robust, production-ready workflows.
        \item Evaluated local vs. remote LLMs for deployment trade-offs, optimizing operational costs by strategically limiting API requests based on latency and accuracy requirements.
    }%
    |||
    {Data Science Trainee}%
    {Digital Egypt Pioneers Initiative (DEPI)}%
    {Jun 2025 - Dec 2025}%
    {%
        \item Completed \textbf{IBM Data Scientist certification} with Python, SQL, and machine learning model families (CNNs, ensemble methods, clustering).
        \item Implemented \textbf{MLOps workflows} using \textbf{MLflow} and \textbf{HuggingFace} for model versioning, experiment tracking, and deployment.
        \item Delivered capstone project with end-to-end ML pipeline including feature engineering, hyperparameter tuning, and model serving.
    }%
    |||
    {Mobile Development Intern (Flutter \& ML)}%
    {Informatique}%
    {Jul 2025 - Aug 2025}%
    {%
        \item Integrated \textbf{Machine Learning models} into mobile applications using \textbf{TFLite} and \textbf{ML Kit} for on-device inference.
        \item Developed cross-platform AI features bridging application logic with ML frameworks for real-time data processing.
    }%
    |||
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Dec 2025}%
    {%
        \item Won \textbf{first place} in a 30+ team hackathon; shipped production features in an agile environment.
        \item Developed complex database queries and optimized data pipelines for a production system handling 1000+ products.
    }%
    |||%
}

% ============================================================
% PROJECTS - Selected for agentic AI / LLM relevance
% ============================================================
\newcommand{\projectsList}{%
    {Mar 2026}%
    {https://github.com/KarimmYasser/sql-station-logistics-chatbot}%
    {Space Station Supply Agent (Agentic AI)}%
    {Built a \textbf{LangGraph}-based conversational AI agent translating natural language into \textbf{SQLite} queries. Engineered an \textbf{autonomous error recovery} system with a self-healing loop and applied \textbf{hallucination detection} guards over token-optimized schemas. Implemented structured output parsing and query validation for reliable tool use.}%
    |||
    {Mar 2026}%
    {https://github.com/KarimmYasser/neo4j-adventure-time-chatbot}%
    {Adventure Time Lore Keeper (Knowledge Graph Agent)}%
    {Developed a conversational agent interacting with a \textbf{Neo4j Knowledge Graph}. Implemented dynamic \textbf{Cypher query generation} with self-healing error recovery, \textbf{conversational memory}, and automated \textbf{entity alias resolution} for consistent multi-turn interactions. Designed the agent's reasoning chain for graph traversal and relationship extraction.}%
    |||
    {Feb 2026}%
    {https://github.com/KarimmYasser/braTs-ai-hackathon-ODCxINSTANT}%
    {BioMedIAMBZ - Brain Tumor Segmentation (1st Place)}%
    {Won \textbf{1st place} in AI Hackathon by building a 3D brain tumor segmentation pipeline using \textbf{MedNeXt} with \textbf{PyTorch} and \textbf{MONAI}. Deployed via \textbf{FastAPI} backend with \textbf{React Native} mobile interface for real-time inference. Engineered a \textbf{40x faster} preprocessing pipeline through optimized data loading.}%
    |||
    {Nov 2025}%
    {https://github.com/KarimmYasser/Walmart-Sales-Forecasting-ML}%
    {Walmart Sales Forecasting - ML Pipeline}%
    {Built an end-to-end \textbf{ML pipeline} with \textbf{44 engineered features} achieving \textbf{99.96\% R²} accuracy. Deployed via \textbf{FastAPI} with \textbf{MLflow} experiment tracking and \textbf{Docker} containerization. Designed modular pipeline architecture for reproducible model training.}%
    |||
    {Nov 2024 - Dec 2024}%
    {https://github.com/KarimmYasser/Slash-Fashion-Assistant-App}%
    {Fashion Assistant - AI-Powered Chatbot Platform}%
    {Built a personalized shopping assistant with an \textbf{NLP-powered chatbot} and intelligent \textbf{product recommendation system}. Integrated conversational AI with structured product data for context-aware responses.}%
    |||
    {Nov 2024 - Dec 2024}%
    {https://github.com/KarimmYasser/sher-look}%
    {Sherlook - Web Search Engine}%
    {Built a search engine with custom \textbf{crawler}, \textbf{indexer}, and \textbf{ranking algorithm} processing \textbf{50K+ pages}. Demonstrates information retrieval fundamentals relevant to RAG pipeline design.}%
    |||%
}

% ============================================================
% TECHNICAL SKILLS - Consolidated for Agentic AI roles
% ============================================================

\newcommand{\skillLanguages}{
Python, SQL, TypeScript, C++, Java, Dart
}

\newcommand{\skillAgenticAI}{
LangChain, LangGraph, RAG Pipelines, Multi-Agent Systems, Prompt Engineering, Hallucination Guards, Tool Orchestration, Conversational Memory, Knowledge Graphs
}

\newcommand{\skillFrameworks}{
PyTorch, HuggingFace, FastAPI, Pydantic, Scikit-learn, Streamlit, MONAI, TFLite/ML Kit
}

\newcommand{\skillData}{
Neo4j, ChromaDB / Vector DBs, PostgreSQL, SQLite, MLflow, Docker, RESTful APIs
}

\newcommand{\skillPractices}{
Agent Architecture, Self-healing Loops, MLOps, Clean Architecture, Structured Output Parsing, Agile/Scrum, Git
}

% ============================================================
% CORE COMPETENCIES - Aligned with Agentic AI culture
% ============================================================

\newcommand{\problemSolving}{
Agent debugging \& reasoning analysis,
System decomposition,
Autonomous error recovery design,
Performance optimization,
Root cause identification
}

\newcommand{\leadership}{
Cross-functional collaboration,
Technical mentoring,
High ownership,
Agile teamwork
}

\newcommand{\communication}{
Technical documentation,
AI explainability,
Knowledge transfer,
Requirements clarification,
Remote collaboration
}

\newcommand{\continuousLearning}{
LLM research adoption,
Rapid prototyping,
Technology adoption,
Industry best practices,
Open-source contributions
}

% ============================================================
