% ============================================================
% RESUME CONTENT - OPTIMIZED FOR SOFTWARE ENGINEER ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{Software Engineer} with over 2 years of experience building scalable applications across mobile, desktop, and web platforms. Proficient in \textbf{Python}, \textbf{C++}, \textbf{Kotlin}, \textbf{Dart}, and \textbf{TypeScript} with a strong foundation in \textbf{data structures}, \textbf{algorithms}, and \textbf{system design}. Proven expertise in clean architecture, agile methodologies, database optimization, and delivering production-ready solutions from conceptualization to deployment.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Dec 2025}%
    {%
        \item Won first place in a 30+ team hackathon, earning a full-time position offer.
        \item Collaborated with back-end engineers and QA testers in an agile environment, analyzing the Flutter desktop app's architecture and state management to guide feature development.
        \item Implemented offline functionality and optimized complex MySQL database queries with direct backend integration for a production system handling over 1000 products.
    }%
    |||
    {Android Developer Intern}%
    {Banque Misr}%
    {Jul 2025 - Sep 2025}%
    {%
        \item Developed native Android applications using Kotlin, Android Jetpack components, and the Room Database for local data persistence.
        \item Implemented MVVM architecture patterns to create scalable and maintainable mobile solutions with enhanced user experience and optimized performance.
    }%
    |||
    {Mobile Development Intern (Flutter \& ML)}%
    {Informatique}%
    {Jul 2025 - Aug 2025}%
    {%
        \item Integrated Machine Learning models into Flutter applications to deliver responsive, intelligent mobile solutions.
        \item Developed cross-platform features by bridging Dart with ML frameworks (e.g., TFLite/ML Kit) for on-device data processing.
    }%
    |||
    {Session Lead}%
    {Udacity (Digital Egypt Cubs Initiative)}%
    {Nov 2025 - Mar 2026}%
    {%
        \item Led weekly sessions for student cohorts, delivering core computer fundamentals and system design principles.
        \item Supported learners through guided code reviews, practical examples, and structured technical discussions.
    }%
    |||%
}

% PROJECTS
\newcommand{\projectsList}{%
    {Jun 2026}%
    {https://github.com/KarimmYasser/GSoCPathfinder}%
    {GSoC Pathfinder - AI Agent Organization Matcher}%
    {Engineered an end-to-end \textbf{FastAPI} and \textbf{React/Vite} application for matching candidate profiles to GSoC organizations. Designed a \textbf{dual-database} architecture using \textbf{Neo4j} and \textbf{Qdrant}. Developed a \textbf{high-performance Rust scoring engine} with \textbf{PyO3} bindings to offload heavy calculations. Implemented a \textbf{LangGraph} agentic workflow and a 2D force-directed \textbf{Knowledge Graph Visualizer}.}%
    |||
    {Mar 2026 - May 2026}%
    {https://github.com/KarimmYasser/aladdin-nasiras-revenge}%
    {Aladdin: Nasira's Revenge - C++ Game Engine}%
    {Developed a high-performance 3D engine using \textbf{C++17} and \textbf{OpenGL 3.3} featuring a data-driven \textbf{Entity Component System (ECS)} with deferred lifecycle management. Engineered a \textbf{command-based renderer} with \textbf{16k shadow mapping} and integrated \textbf{miniaudio} and \textbf{FFmpeg} for disk-streamed media.}%
    |||
    {Feb 2026 - Mar 2026}%
    {https://github.com/KarimmYasser/rusty-sherlook-engine}%
    {Rusty Sherlook - High-Performance Search Engine}%
    {Engineered a high-concurrency extension to the Sherlook search engine in \textbf{Rust} utilizing \textbf{Tokio}. Integrated \textbf{Qdrant} for semantic vector search and \textbf{Neo4j} for advanced graph-based PageRank processing.}%
    |||
    {Jun 2025}%
    {https://github.com/KarimmYasser/isupply_app}%
    {i'Supply POS App - First Place Hackathon Winner}%
    {Developed a cross-platform \textbf{Flutter POS system} for desktop and mobile, featuring inventory search, cart management, and invoice tracking. Integrated \textbf{Hive} for local storage and \textbf{Supabase} backend with offline synchronization.}%
    |||
    {Mar 2026 - Apr 2026}%
    {https://github.com/KarimmYasser/ai-eval-framework}%
    {AI API Evaluation Framework}%
    {Engineered a high-performance \textbf{FastAPI} orchestrator with \textbf{SSE streaming} for real-time monitoring of AI agents. Developed an \textbf{Agent Trace Viewer} for multi-turn loops, enabling granular credit assignment across reasoning and tool-calling steps.}%
    |||
    {Apr 2026 - May 2026}%
    {https://github.com/KarimmYasser/robot-wall-follower}%
    {Autonomous Wall-Following Robot}%
    {Developed professional-grade \textbf{bare-metal C} firmware for ATmega328P utilizing \textbf{Timer1} and \textbf{EXTI/PCINT} interrupts for non-blocking sensing. Designed a \textbf{Cascaded PID Controller} nesting a wall-distance loop within an IMU heading loop.}%
    |||
    {Oct 2025 - Dec 2025}%
    {https://github.com/KarimmYasser/yapper-mobile}%
    {Yapper - Cross-Platform Mobile App}%
    {Built a full-stack social media application utilizing \textbf{React Native} and \textbf{Expo}. Implemented real-time messaging via \textbf{WebSockets}, multi-language \textbf{RTL} support, and automated deployments with a comprehensive \textbf{CI/CD} pipeline.}%
    |||%
}

% TECHNICAL SKILLS
\newcommand{\programmingLanguages}{Python, C++, C, Kotlin, Dart, Java, TypeScript, JavaScript, SQL}
\newcommand{\mobileDevelopment}{}
\newcommand{\frameworksLibraries}{Flutter Bloc, Riverpod, Dagger/Hilt, Room, Retrofit, FastAPI, Scikit-learn, Pandas, Node.js}
\newcommand{\backendDatabase}{Supabase, Firebase, MySQL, PostgreSQL, SQLite, Offline-first Architecture, API Integration}
\newcommand{\developmentTools}{Git, GitHub, Docker, Linux, VS Code, CI/CD, Agile/Scrum}
\newcommand{\softwareEngineering}{Clean Architecture, MVVM, SOLID Principles, Dependency Injection, State Management, Object-Oriented Programming (OOP), Design Patterns}
\newcommand{\dataScience}{}
\newcommand{\artificialIntelligence}{}
\newcommand{\researchSkills}{}
\newcommand{\specializedSkills}{}

% CORE COMPETENCIES
\newcommand{\problemSolving}{Analytical thinking, Problem decomposition, Algorithm design, Debugging, Root cause identification}
\newcommand{\leadership}{Technical mentoring, Code review, Cross-functional collaboration, Agile teamwork}
\newcommand{\communication}{Technical documentation, Knowledge transfer, Remote collaboration}
\newcommand{\continuousLearning}{Technology adoption, Industry best practices, Rapid skill acquisition}
% ============================================================

