% ============================================================
% RESUME CONTENT - OPTIMIZED FOR AI ENGINEER ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{AI Engineer} with hands-on experience integrating robust AI/ML solutions into production applications. IBM certified with expertise in \textbf{Python}, \textbf{TensorFlow}, \textbf{HuggingFace}, and advanced \textbf{NLP}. Experienced in deploying on-device AI using TFLite/ML Kit, building intelligent chatbots, and implementing high-accuracy predictive systems. Strong foundation in MLOps, model optimization, and scalable inference via FastAPI and containerization.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Mobile Development Intern (Flutter \& ML)}%
    {Informatique}%
    {Jul 2025 - Aug 2025}%
    {%
        \item Integrated Machine Learning models into mobile applications for intelligent, responsive user solutions.
        \item Developed cross-platform AI features utilizing TFLite and ML Kit to enable real-time, on-device data processing and inference.
    }%
    |||
    {Data Science Trainee}%
    {Digital Egypt Pioneers Initiative (DEPI)}%
    {Jun 2025 - Dec 2025}%
    {%
        \item Completed IBM Data Scientist certification covering Python, advanced statistics, and machine learning.
        \item Implemented MLOps workflows using MLflow and HuggingFace to orchestrate model versioning and reliable deployment.
    }%
    |||
    {Flutter Developer Intern}%
    {SlashHub}%
    {Oct 2024 - Jan 2025}%
    {%
        \item Designed an AI-powered e-commerce chatbot incorporating NLP integration and dynamic product recommendations.
        \item Achieved a 25\% improvement in user engagement through carefully architected intelligent conversation flows.
    }%
    |||
    {Agentic AI Trainee}%
    {Orange Digital Center Egypt}%
    {Feb 2026 - Apr 2026}%
    {%
        \item Built autonomous AI agents using LangChain/LangGraph, establishing memory and multi-turn collaboration pipelines.
    }%
    |||%
}

% PROJECTS
\newcommand{\projectsList}{%
    {Jun 2026}%
    {https://github.com/KarimmYasser/GSoCPathfinder}%
    {GSoC Pathfinder - AI Agent Organization Matcher}%
    {Built an \textbf{AI matching engine} canonicalizing 11 years of GSoC data using \textbf{Neo4j} and \textbf{Qdrant} for semantic vector search. Engineered a \textbf{LangGraph} agent pipeline and a \textbf{high-performance Rust scoring engine} implementing a \textbf{7-Factor weighted ranking} (Skill Overlap, Semantic Similarity). Developed a \textbf{React} dashboard with CV gap analysis and LLM-driven roadmap optimization.}%
    |||
    {Mar 2026 - May 2026}%
    {https://github.com/KarimmYasser/machine-sound-classification}%
    {Industrial Machine Sound Classification}%
    {Architected a Dual-Track AI pipeline achieving \textbf{95.61\% accuracy} using an XGBoost edge champion and EfficientAT cloud model. Engineered a Rust extraction engine for \textbf{57x faster feature extraction}.}%
    |||
    {Mar 2026 - Apr 2026}%
    {https://github.com/KarimmYasser/ai-eval-framework}%
    {AI API Evaluation Framework}%
    {Engineered an evaluation platform for Multimodal AI and Agentic Workflows. Built an \textbf{Agent Trace Viewer} for multi-turn loops to enable granular credit assignment and detailed model fidelity analysis.}%
    |||
    {Nov 2025}%
    {https://github.com/KarimmYasser/Walmart-Sales-Forecasting-ML}%
    {Walmart Sales Forecasting - AI Pipeline}%
    {Built an end-to-end AI pipeline achieving \textbf{99.96\% R² accuracy}, deployed via \textbf{FastAPI} with \textbf{MLflow tracking} and \textbf{Docker} containerization for reproducibility.}%
    |||
    {Oct 2025 - Dec 2025}%
    {https://github.com/KarimmYasser/yapper-mobile}%
    {Yapper - AI-Powered Social Media App}%
    {Built a cross-platform React Native app featuring real-time WebSocket messaging and \textbf{AI-powered tweet summarization}.}%
    |||
    {Feb 2026}%
    {https://github.com/KarimmYasser/braTs-ai-hackathon-ODCxINSTANT}%
    {BioMedIAMBZ - Brain Tumor Segmentation (1st Place)}%
    {Won 1st place in an AI Hackathon by developing a 3D medical imaging segmentation pipeline using \textbf{MedNeXt} with \textbf{PyTorch}.}%
    |||
    {Jul 2025 - Aug 2025}%
    {https://github.com/KarimmYasser/school_scheduler}%
    {AI Timetable Generator}%
    {Developed an AI-driven constraint satisfaction optimizer using \textbf{Google OR-Tools} to automate complex scheduling.}%
    |||%
}

% TECHNICAL SKILLS
\newcommand{\programmingLanguages}{Python, C++, SQL, Java, Rust}
\newcommand{\mobileDevelopment}{}
\newcommand{\frameworksLibraries}{TensorFlow, PyTorch, Hugging Face, Transformers, Scikit-learn, LangChain, FastAPI, Streamlit}
\newcommand{\backendDatabase}{}
\newcommand{\developmentTools}{}
\newcommand{\softwareEngineering}{AI Pipelines, MLOps, Model Serving, Microservices, Clean Architecture}
\newcommand{\dataScience}{Feature Engineering, Data Preprocessing, Model Evaluation, Exploratory Data Analysis}
\newcommand{\artificialIntelligence}{Natural Language Processing (NLP), Deep Learning, Recommendation Systems, Neural Networks}
\newcommand{\researchSkills}{}
\newcommand{\specializedSkills}{}

% CORE COMPETENCIES
\newcommand{\problemSolving}{AI system design, Model debugging, Performance optimization}
\newcommand{\leadership}{Cross-functional collaboration, Agile teamwork, Technical Mentoring}
\newcommand{\communication}{Technical documentation, AI explainability, Knowledge transfer}
\newcommand{\continuousLearning}{Research papers, Technology adoption, Industry trends}
% ============================================================

