% ============================================================
% RESUME CONTENT - OPTIMIZED FOR C++ DEVELOPER ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{C++ Developer} with a strong foundation in object-oriented programming, low-level data structures, and algorithms. Experienced in building high-performance applications, 3D game engines, and operating system simulators. Proficient in strict memory management, concurrent processing, and systems programming. Solid background in embedded systems, hardware description languages (Verilog/VHDL), and bridging bare-metal firmware with complex algorithms.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Dec 2025}%
    {%
        \item Won first place in a 30+ team hackathon, earning a full-time position offer.
        \item Developed highly scalable software solutions and optimized complex database queries with a strict focus on system performance and high code quality standards.
    }%
    |||
    {Android Developer Intern}%
    {Banque Misr}%
    {Jul 2025 - Sep 2025}%
    {%
        \item Developed native applications using strong OOP principles, Clean Architecture, and well-established design patterns.
    }%
    |||
    {Data Science Trainee}%
    {Digital Egypt Pioneers Initiative (DEPI)}%
    {Jun 2025 - Dec 2025}%
    {%
        \item Applied advanced algorithmic approaches and optimized data structures to process large-scale data pipelines efficiently.
    }%
    |||
    {Session Lead}%
    {Udacity (Digital Egypt Cubs Initiative - DECI)}%
    {Nov 2025 - Mar 2026}%
    {%
        \item Led weekly sessions delivering core computer fundamentals including memory allocation, processes, and algorithms.
    }%
    |||%
}

% PROJECTS
\newcommand{\projectsList}{%
    {Feb 2026 - Mar 2026}%
    {https://github.com/KarimmYasser/rusty-sherlook-engine}%
    {Rusty Sherlook - High-Performance Search Engine}%
    {Engineered a high-concurrency extension to the Sherlook search engine in \textbf{Rust} utilizing \textbf{Tokio}. Integrated \textbf{Qdrant} for semantic vector search and \textbf{Neo4j} for advanced graph-based PageRank processing.}%
    |||
    {Mar 2026 - May 2026}%
    {https://github.com/KarimmYasser/aladdin-nasiras-revenge}%
    {Aladdin: Nasira's Revenge - C++ Game Engine}%
    {Developed a high-performance 3D engine using \textbf{C++17} and \textbf{OpenGL 3.3} featuring a data-driven \textbf{Entity Component System (ECS)} with deferred lifecycle management for memory stability. Integrated \textbf{miniaudio} and \textbf{FFmpeg} for BGM and video streaming.}%
    |||
    {Feb 2024 - Apr 2024}%
    {https://github.com/KarimmYasser/Alien_Invasion_Project}%
    {Alien Invasion - C++ Game}%
    {Developed a complete game in \textbf{C++} using advanced OOP principles, implementing linked lists, queues, and stacks from scratch for rigorous entity management.}%
    |||
    {Feb 2025}%
    {https://github.com/KarimmYasser/cmpsh}%
    {Unix Shell Implementation}%
    {Implemented a lightweight Unix shell in \textbf{C} utilizing system calls for process management (fork/exec), inter-process communication via pipes, I/O redirection, and robust signal handling.}%
    |||
    {Mar 2025 - May 2025}%
    {https://github.com/KarimmYasser/kernel-sim-ohh-s}%
    {Operating System Scheduler}%
    {Developed an OS process scheduler simulator in \textbf{C} implementing complex scheduling algorithms (FCFS, SJF, Priority, Round Robin) with real-time visualization.}%
    |||
    {Apr 2026 - May 2026}%
    {https://github.com/KarimmYasser/robot-wall-follower}%
    {Autonomous Wall-Following Robot}%
    {Engineered \textbf{bare-metal C} firmware for ATmega328P with a Cascaded PID Controller utilizing Timer1 and EXTI/PCINT interrupts for non-blocking sensor integration.}%
    |||
    {Nov 2023 - Jan 2024}%
    {https://github.com/KarimmYasser/paint-for-kids}%
    {Paint for Kids - C++ Desktop Application}%
    {Built a Qt-based drawing application extensively utilizing polymorphism, inheritance, and GoF design patterns.}%
    |||%
}

% TECHNICAL SKILLS
\newcommand{\programmingLanguages}{\textbf{C++}, \textbf{C}, Python, Rust, Java, Dart, SQL}
\newcommand{\mobileDevelopment}{}
\newcommand{\frameworksLibraries}{STL, OpenGL, Make, CMake, Assimp}
\newcommand{\backendDatabase}{}
\newcommand{\developmentTools}{Git, GDB, Valgrind, VS Code, Visual Studio}
\newcommand{\softwareEngineering}{Object-Oriented Programming (OOP), Memory Management, Systems Programming, Clean Architecture}
\newcommand{\dataScience}{}
\newcommand{\artificialIntelligence}{}
\newcommand{\researchSkills}{}
\newcommand{\specializedSkills}{Embedded C, Bare-Metal Drivers, Computer Graphics, Operating Systems}

% CORE COMPETENCIES
\newcommand{\problemSolving}{Algorithm design, Data structure optimization, Performance profiling, Pointer debugging}
\newcommand{\leadership}{Code review, Mentoring, Team collaboration}
\newcommand{\communication}{Technical documentation, Code readability}
\newcommand{\continuousLearning}{Modern C++17 standards, System design, Low-level optimization}
% ============================================================

