% ============================================================
% RESUME CONTENT - OPTIMIZED FOR DATA ANALYST ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{Data Analyst} with hands-on experience in complex data analysis, interactive visualization, and business intelligence. IBM certified with expertise in \textbf{Python}, \textbf{SQL}, \textbf{Pandas}, and leading data visualization tools. Proven ability to extract actionable insights from messy datasets, build intuitive \textbf{Streamlit} dashboards, and support data-driven decision making. Strong foundation in statistical analysis, ETL processes, data cleaning, and effectively communicating findings to stakeholders.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Data Science Trainee}%
    {Digital Egypt Pioneers Initiative (DEPI)}%
    {Jun 2025 - Dec 2025}%
    {%
        \item Completed IBM Data Scientist certification covering Python, SQL, and robust data analysis techniques.
        \item Performed exploratory data analysis (EDA) and rigorous feature engineering on multiple real-world datasets.
        \item Delivered a capstone project showcasing comprehensive data visualization and actionable business insights.
    }%
    |||
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Dec 2025}%
    {%
        \item Developed complex SQL queries for an offline MySQL server, performing database analysis and optimization.
        \item Collaborated closely with stakeholders to analyze business requirements and deliver data-driven solutions for a system handling thousands of products.
    }%
    |||
    {Resource Management Team Member}%
    {Enactus Cairo University}%
    {Dec 2025 - Feb 2026}%
    {%
        \item Engaged in survey design, market research, and targeted data collection for effective problem validation.
        \item Analyzed research data quantitatively to ensure proposed solution relevance and feasibility before project kickoff.
    }%
    |||%
}

% PROJECTS
\newcommand{\projectsList}{%
    {Jun 2026}%
    {https://github.com/KarimmYasser/GSoCPathfinder}%
    {GSoC Pathfinder - AI Agent Organization Matcher}%
    {Canonicalized and analyzed 11 years of historical GSoC data (663 organizations, 12k+ projects) to build an \textbf{AI Agent matching engine}. Developed a \textbf{7-Factor ranking model} to evaluate candidate profiles. Built an interactive \textbf{React/Vite dashboard} with a 2D \textbf{Knowledge Graph Visualizer} and automated CV gap analysis.}%
    |||
    {Jun 2025}%
    {https://github.com/KarimmYasser/music_store_analysis}%
    {Music Store Business Data Analysis}%
    {Conducted a comprehensive data analysis of music store sales records using \textbf{Python} and \textbf{pandas}. Performed extensive \textbf{data cleaning}, integration, and generated key \textbf{business insights} supported by clear visualizations.}%
    |||
    {Nov 2025}%
    {https://github.com/KarimmYasser/Walmart-Sales-Forecasting-ML}%
    {Walmart Sales Forecasting Analysis}%
    {Analyzed extensive historical sales data across 45 stores, performing robust \textbf{EDA} and \textbf{feature engineering}. Built interactive \textbf{Streamlit} dashboards to present actionable business insights to potential stakeholders.}%
    |||
    {Sep 2025}%
    {https://github.com/KarimmYasser/heart_disease_prediction}%
    {Heart Disease Data Analysis}%
    {Performed comprehensive data analysis on health records including preprocessing, statistical evaluation, \textbf{feature selection}, and visualization, ultimately presented via an interactive web dashboard.}%
    |||
    {Sep 2025}%
    {https://github.com/KarimmYasser/wuzzuf-job-scraper}%
    {Wuzzuf Jobs Market Data Scraper}%
    {Developed a reliable \textbf{data collection} pipeline using \textbf{Python} and \textbf{Selenium} to automatically extract engineering job market data and export it into structured CSV/JSON formats for further analysis.}%
    |||
    {Aug 2025 - Sep 2025}%
    {https://github.com/KarimmYasser/FollowersInstagram}%
    {Instagram Followers Analyzer}%
    {Developed a dedicated desktop application to parse and \textbf{analyze} Instagram data exports, generating automated follower insights and interaction metrics.}%
    |||
    {Mar 2025 - May 2025}%
    {https://github.com/KarimmYasser/sher-look}%
    {Sherlook Web Indexing Engine}%
    {Built a custom web scraper and search engine processing over 50K+ pages, implementing custom data indexing and \textbf{ranking algorithms} for efficient information retrieval.}%
    |||%
}

% TECHNICAL SKILLS
\newcommand{\programmingLanguages}{Python, SQL, R, JavaScript}
\newcommand{\mobileDevelopment}{}
\newcommand{\frameworksLibraries}{Pandas, NumPy, Matplotlib, Seaborn, Plotly, Streamlit, Selenium, BeautifulSoup}
\newcommand{\backendDatabase}{MySQL, SQLite, PostgreSQL, Query Optimization, Database Design, Relational Databases}
\newcommand{\developmentTools}{Jupyter Notebooks, Excel, Git, GitHub, VS Code, Postman}
\newcommand{\softwareEngineering}{}
\newcommand{\dataScience}{Exploratory Data Analysis (EDA), Data Cleaning, Data Visualization, Statistical Analysis, Data Wrangling}
\newcommand{\artificialIntelligence}{}
\newcommand{\researchSkills}{}
\newcommand{\specializedSkills}{}

% CORE COMPETENCIES
\newcommand{\problemSolving}{Analytical thinking, Statistical reasoning, Problem decomposition, Root cause identification}
\newcommand{\leadership}{Cross-functional collaboration, Stakeholder management, Agile teamwork}
\newcommand{\communication}{Data storytelling, Dashboard creation, Technical documentation, Stakeholder presentations}
\newcommand{\continuousLearning}{Technology adoption, Industry best practices, Rapid skill acquisition}
% ============================================================

