% ============================================================
% RESUME CONTENT - OPTIMIZED FOR HARDWARE DEVELOPER ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{Hardware \& Embedded Systems Engineer} with practical experience in FPGA design, bare-metal C programming, and microprocessor architectures. Highly proficient in \textbf{Verilog}, \textbf{VHDL}, and \textbf{C/C++}. Experienced in designing custom hardware accelerators, complex pipelined processors, and developing robust embedded firmware for autonomous systems. Strong foundation in VLSI design flow, RTL-to-GDSII logic synthesis, and real-time control system implementation.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Session Lead}%
    {Udacity (Digital Egypt Cubs Initiative - DECI)}%
    {Nov 2025 - Mar 2026}%
    {%
        \item Led weekly sessions delivering core computer fundamentals, focusing heavily on system architecture, memory hierarchies, and digital logic design principles.
        \item Mentored students through practical exercises demonstrating the interaction between low-level software and physical hardware.
    }%
    |||
    {Resource Management Team Member}%
    {Enactus Cairo University}%
    {Dec 2025 - Feb 2026}%
    {%
        \item Supported rigorous planning and resource allocation for hardware-oriented engineering projects and physical prototypes.
        \item Validated technical feasibility of proposed hardware systems through structured ideation methodologies.
    }%
    |||
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Dec 2025}%
    {%
        \item Gained extensive experience in system-level architecture and performance optimization, translating high-level requirements into scalable designs.
    }%
    |||%
}

% PROJECTS
\newcommand{\projectsList}{%
    {Apr 2026 - May 2026}%
    {https://github.com/KarimmYasser/robot-wall-follower}%
    {Autonomous Wall-Following Robot (Sim-to-Real)}%
    {Engineered highly-optimized bare-metal \textbf{C} firmware for the \textbf{ATmega328P} utilizing \textbf{Timer1} and \textbf{EXTI/PCINT} interrupts. Designed a \textbf{Cascaded PID Controller} nesting wall-distance within an IMU heading loop for exact 90° pivots and integrated Bluetooth telemetry.}%
    |||
    {Nov 2025 - Dec 2025}%
    {https://github.com/KarimmYasser/VLSI-Convolution-Systolic-Accelerator}%
    {VLSI Convolution Systolic Accelerator}%
    {Designed a high-performance 2D convolution accelerator in \textbf{Verilog} using an 8x8 systolic array targeting the \textbf{SKY130 PDK}. Successfully executed the complete \textbf{RTL-to-GDSII} flow via \textbf{OpenLane}.}%
    |||
    {Oct 2025 - Dec 2025}%
    {https://github.com/KarimmYasser/stall_3alda2ery}%
    {5-Stage Pipelined Processor}%
    {Designed a complete 32-bit 5-stage pipelined MIPS processor in \textbf{VHDL} supporting hardware interrupts and mapped I/O. Implemented robust hazard handling via data forwarding and built a custom Python assembler.}%
    |||
    {Feb 2024 – Apr 2024}%
    {https://github.com/KarimmYasser/AES}%
    {AES Encryption – FPGA Implementation}%
    {Redesigned the AES-128/192/256 algorithm in \textbf{Verilog} for FPGA deployment, achieving \textbf{40\% faster encryption} throughput using advanced pipelining and hardware parallelism.}%
    |||
    {Dec 2025}%
    {https://github.com/KarimmYasser/FM_Stereo_System}%
    {FM Stereo Broadcasting System Simulation}%
    {Implemented a software-defined FM Stereo Transmitter and Receiver, conducting experimental analysis on frequency deviation, noise immunity, and system robustness in noisy channel environments.}%
    |||
    {Feb 2025}%
    {https://github.com/KarimmYasser/cmpsh}%
    {Unix Shell - System Architecture}%
    {Implemented a Unix shell in C utilizing direct system calls, demonstrating deep understanding of OS process execution, interrupts, and I/O handling.}%
    |||%
}

% TECHNICAL SKILLS
\newcommand{\programmingLanguages}{C, C++, Assembly, Python, MATLAB}
\newcommand{\mobileDevelopment}{}
\newcommand{\frameworksLibraries}{OpenLane, Yosys, Magic, GTKWave}
\newcommand{\backendDatabase}{}
\newcommand{\developmentTools}{ModelSim, Quartus, Vivado, Proteus, Webots, Make}
\newcommand{\softwareEngineering}{VLSI Design, RTL-to-GDSII, Pipelining, Hazard Handling}
\newcommand{\dataScience}{}
\newcommand{\artificialIntelligence}{}
\newcommand{\researchSkills}{}
\newcommand{\specializedSkills}{Hardware Accelerators, Systolic Arrays, Power/Timing Analysis}

% CORE COMPETENCIES
\newcommand{\problemSolving}{Hardware debugging, Timing analysis, Power/Area optimization}
\newcommand{\leadership}{Technical collaboration, Project planning}
\newcommand{\communication}{Hardware documentation, Design presentations}
\newcommand{\continuousLearning}{Adopting new PDKs, Architecture exploration, Reading datasheets}
% ============================================================

