% ============================================================
% RESUME CONTENT - OPTIMIZED FOR DATA ENGINEER ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{Data Engineer} with experience building data pipelines, ETL processes, and database systems. Proficient in \textbf{Python}, \textbf{SQL}, and \textbf{Docker} with hands-on experience in database optimization, offline-first architectures, and API integration. Strong foundation in designing scalable data infrastructure, implementing MLOps workflows with MLflow, and deploying data applications via FastAPI. Experienced in agile environments with proven ability to optimize query performance and manage production databases.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Present}%
    {%
        \item Won first place in a 30+ team hackathon, earning a full-time position offer.
        \item Developed complex queries for an offline MySQL server, including optimization and direct interaction with the live backend database.
        \item Implemented offline-first data synchronization architecture for desktop and mobile applications.
        \item Gained hands-on experience in database management and performance tuning.
    }%
    |||
    {Data Science Trainee}%
    {Digital Egypt Pioneers Initiative (DEPI)}%
    {Jun 2025 - Dec 2025}%
    {%
        \item Completed IBM Data Scientist certification with Python and SQL.
        \item Implemented MLOps workflows using MLflow for model versioning and deployment pipelines.
        \item Built end-to-end data pipelines with Docker containerization.
    }%
    |||
    {Mobile Development Intern}%
    {Informatique}%
    {Jul 2025 - Aug 2025}%
    {%
        \item Developed data processing pipelines bridging applications with ML frameworks for on-device inference.
    }%
    |||%
}

% PROJECTS
\newcommand{\projectsList}{%
    {Nov 2025}%
    {https://github.com/KarimmYasser/Walmart-Sales-Forecasting-ML}%
    {Walmart Sales Forecasting - Data Pipeline}%
    {Built an end-to-end \textbf{data pipeline} for sales forecasting, featuring \textbf{44 engineered features}, \textbf{FastAPI} serving layer, \textbf{MLflow} tracking, and \textbf{Docker} containerization for deployment.}%
    |||
    {Jun 2025}%
    {https://github.com/KarimmYasser/isupply_app}%
    {i'Supply POS - Offline Data Architecture}%
    {Designed \textbf{offline-first data architecture} with \textbf{Hive} local storage and \textbf{Supabase} backend synchronization, supporting 1000+ products with efficient data pagination.}%
    |||
    {Mar 2025 – May 2025}%
    {https://github.com/KarimmYasser/sher-look}%
    {Sherlook Web Engine - Data Pipeline}%
    {Built a search engine with custom \textbf{web crawler}, data \textbf{indexer}, and \textbf{ranking algorithm} processing and storing 50K+ pages.}%
    |||
    {Sep 2025}%
    {https://github.com/KarimmYasser/wuzzuf-job-scraper}%
    {Wuzzuf Jobs Data Scraper}%
    {Developed a \textbf{data extraction pipeline} using Python and Selenium to collect job listings and export to structured formats (CSV/JSON).}%
    |||
    {Sep 2025}%
    {https://github.com/KarimmYasser/heart_disease_prediction}%
    {Heart Disease Prediction Pipeline}%
    {Built an \textbf{ETL pipeline} for healthcare data with preprocessing, feature engineering, and model deployment.}%
    |||
    {Aug 2025}%
    {https://github.com/KarimmYasser/flight_reservation_desktop}%
    {Flight Reservation Database System}%
    {Developed a \textbf{database-driven} CRUD application with \textbf{SQLite} for persistent data storage.}%
    |||
    {Jun 2025}%
    {https://github.com/KarimmYasser/music_store_analysis}%
    {Music Store Data Analysis}%
    {Built \textbf{data integration} pipelines using Python and pandas for multi-source data cleaning and analysis.}%
    |||%
}

% TECHNICAL SKILLS
\newcommand{\programmingLanguages}{
Python,
SQL,
Java,
Bash
}

\newcommand{\mobileDevelopment}{}

\newcommand{\frameworksLibraries}{
Pandas,
NumPy,
FastAPI,
SQLAlchemy,
Selenium,
PySpark
}

\newcommand{\backendDatabase}{
MySQL,
PostgreSQL,
SQLite,
Supabase,
Firebase,
Database Design,
Query Optimization,
Data Modeling,
Indexing
}

\newcommand{\developmentTools}{
Docker,
Git,
GitHub,
MLflow,
Jupyter Notebooks,
VS Code,
Linux,
CI/CD
}

\newcommand{\softwareEngineering}{
ETL Pipelines,
Data Warehousing,
API Development,
Microservices,
Offline-first Architecture
}

\newcommand{\dataScience}{
Data Modeling,
Data Cleaning,
Feature Engineering,
Data Integration
}

\newcommand{\artificialIntelligence}{
MLOps,
Model Deployment,
Pipeline Orchestration
}

\newcommand{\researchSkills}{}

\newcommand{\specializedSkills}{
Algorithms,
Data Structures,
Distributed Systems
}

% CORE COMPETENCIES
\newcommand{\problemSolving}{
Analytical thinking,
System design,
Performance optimization,
Root cause identification
}

\newcommand{\leadership}{
Cross-functional collaboration,
Agile teamwork
}

\newcommand{\communication}{
Technical documentation,
Knowledge transfer,
Stakeholder collaboration
}

\newcommand{\continuousLearning}{
Technology adoption,
Industry best practices,
Rapid skill acquisition
}

% ============================================================
