% ============================================================
% RESUME CONTENT - OPTIMIZED FOR DATA SCIENTIST ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{Data Scientist} with hands-on experience in end-to-end machine learning pipelines, statistical analysis, and data-driven decision making. IBM certified with expertise in \textbf{Python}, \textbf{SQL}, \textbf{Scikit-learn}, \textbf{Pandas}, and \textbf{NumPy}. Proven ability to deliver production ML models with 99.96\% accuracy, implement MLOps workflows using MLflow and Docker, and communicate insights through interactive dashboards. Strong foundation in feature engineering, model optimization, and business analytics.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Data Science Trainee}%
    {Digital Egypt Pioneers Initiative (DEPI)}%
    {Jun 2025 - Dec 2025}%
    {%
        \item Completed IBM Data Scientist certification with Python, SQL, and machine learning.
        \item Implemented MLOps workflows using MLflow and HuggingFace for model deployment.
        \item Delivered a capstone project applying an end-to-end ML pipeline for business solutions.
    }%
    |||
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Present}%
    {%
        \item Won first place in a 30+ team hackathon, earning a full-time position offer.
        \item Developed complex SQL queries for database optimization and performance tuning.
    }%
    |||
    {Mobile Development Intern (Flutter \& ML)}%
    {Informatique}%
    {Jul 2025 - Aug 2025}%
    {%
        \item Integrated Machine Learning models into applications using TFLite/ML Kit for on-device inference.
    }%
    |||
    {Resource Management Team Member}%
    {Enactus Cairo University}%
    {Dec 2025 - Present}%
    {%
        \item Engaged in problem validation processes including survey design, market research, and data collection.
    }%
    |||%
}

% PROJECTS
\newcommand{\projectsList}{%
    {Nov 2025}%
    {https://github.com/KarimmYasser/Walmart-Sales-Forecasting-ML}%
    {Walmart Sales Forecasting - ML Pipeline}%
    {Developed an end-to-end \textbf{ML pipeline} for weekly sales forecasting across 45 stores, achieving \textbf{99.96\% R²} accuracy with \textbf{Random Forest}. Built 44 engineered features, deployed via \textbf{FastAPI} and \textbf{Streamlit} with \textbf{MLflow} tracking and \textbf{Docker} containerization.}%
    |||
    {Sep 2025}%
    {https://github.com/KarimmYasser/heart_disease_prediction}%
    {Heart Disease Prediction Pipeline}%
    {Engineered an end-to-end machine learning pipeline for heart disease prediction, from \textbf{data preprocessing} and \textbf{feature selection} to model tuning and deployment via an interactive \textbf{Streamlit} web app.}%
    |||
    {Jun 2025}%
    {https://github.com/KarimmYasser/music_store_analysis}%
    {Music Store Analysis}%
    {Conducted a comprehensive \textbf{data analysis} of music store sales using \textbf{Python} and \textbf{pandas}, performing data cleaning, integration, and generating key business insights.}%
    |||
    {Sep 2025}%
    {https://github.com/KarimmYasser/wuzzuf-job-scraper}%
    {Wuzzuf Engineering Jobs Scraper}%
    {Developed a web scraper using \textbf{Python} and \textbf{Selenium} to automatically extract engineering job listings and export structured data to CSV/JSON.}%
    |||
    {Jul 2025 - Aug 2025}%
    {https://github.com/KarimmYasser/school_scheduler}%
    {School Timetable Generator}%
    {Developed an AI-driven school timetable generator using \textbf{Google OR-Tools} for constraint satisfaction optimization.}%
    |||
    {Nov 2024 - Dec 2024}%
    {https://github.com/KarimmYasser/Slash-Fashion-Assistant-App}%
    {Fashion Assistant - E-commerce Platform}%
    {Built a personalized shopping assistant with AI-powered chatbot and \textbf{product recommendation system}.}%
    |||
    {Mar 2025 – May 2025}%
    {https://github.com/KarimmYasser/sher-look}%
    {Sherlook Web Engine}%
    {Built a web search engine with custom crawler, indexer, and \textbf{ranking algorithm} processing 50K+ pages.}%
    |||%
}

% TECHNICAL SKILLS
\newcommand{\programmingLanguages}{
Python,
SQL,
R,
Java
}

\newcommand{\mobileDevelopment}{}

\newcommand{\frameworksLibraries}{
Scikit-learn,
Pandas,
NumPy,
SciPy,
Matplotlib,
Seaborn,
Streamlit,
FastAPI,
TensorFlow,
Selenium
}

\newcommand{\backendDatabase}{
MySQL,
SQLite,
PostgreSQL,
Database Design,
Query Optimization,
Data Warehousing
}

\newcommand{\developmentTools}{
Jupyter Notebooks,
Git,
GitHub,
Docker,
MLflow,
Hugging Face,
VS Code,
Web Scraping
}

\newcommand{\softwareEngineering}{
ML Pipelines,
ETL Processes,
Data Modeling,
Statistical Analysis
}

\newcommand{\dataScience}{
Exploratory Data Analysis (EDA),
Feature Engineering,
Feature Selection,
Dimensionality Reduction (PCA),
Data Cleaning,
Data Visualization,
Statistical Testing
}

\newcommand{\artificialIntelligence}{
Supervised Learning,
Unsupervised Learning,
Random Forest,
XGBoost,
Support Vector Machines (SVM),
Clustering Algorithms,
Hyperparameter Tuning,
Cross-Validation
}

\newcommand{\researchSkills}{
Survey Design,
Problem Validation,
Market Research,
Data Collection,
Literature Review,
A/B Testing
}

\newcommand{\specializedSkills}{
Algorithms,
Data Structures
}

% CORE COMPETENCIES
\newcommand{\problemSolving}{
Analytical thinking,
Statistical reasoning,
Problem decomposition,
Root cause identification
}

\newcommand{\leadership}{
Technical mentoring,
Cross-functional collaboration,
Agile teamwork
}

\newcommand{\communication}{
Data storytelling,
Technical documentation,
Stakeholder presentations,
Knowledge transfer
}

\newcommand{\continuousLearning}{
Technology adoption,
Industry best practices,
Rapid skill acquisition
}

% ============================================================
