% ============================================================
% RESUME CONTENT - OPTIMIZED FOR FLUTTER DEVELOPER ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{Flutter Developer} with 2+ years of experience building cross-platform mobile and desktop applications. Proven expertise in Flutter state management (\textbf{Bloc}, \textbf{Riverpod}, \textbf{Provider}), clean architecture, and offline-first development. Strong track record in delivering production-ready apps with \textbf{Firebase}, \textbf{Supabase}, and RESTful API integration. Experience teaching Flutter to 30+ students and leading agile development teams.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Present}%
    {%
        \item Won first place in a 30+ team hackathon, earning a full-time position offer.
        \item Collaborated with back-end engineers and QA testers in an agile environment, analyzing the Flutter desktop app's architecture and state management to guide feature development.
        \item Implemented offline functionality, fixed existing bugs, and added small features for the first release.
    }%
    |||
    {Android Developer Intern}%
    {Banque Misr}%
    {Jul 2025 - Sep 2025}%
    {%
        \item Developed native Android applications using Kotlin, Jetpack components, Room Database, and MVVM architecture for scalable mobile solutions.
    }%
    |||
    {Mobile Development Intern (Flutter \& ML)}%
    {Informatique}%
    {Jul 2025 - Aug 2025}%
    {%
        \item Integrated ML models into Flutter apps using TFLite/ML Kit for on-device data processing.
    }%
    |||
    {Data Science Trainee}%
    {Digital Egypt Pioneers Initiative (DEPI)}%
    {Jun 2025 - Dec 2025}%
    {%
        \item Completed IBM Data Scientist certification; delivered capstone project with end-to-end ML pipeline.
    }%
    |||
    {Flutter Instructor}%
    {IEEE Cairo University SB}%
    {Feb 2025 - May 2025}%
    {%
        \item Instructed 30+ students in Flutter development, state management, and API integration with 90\% satisfaction.
    }%
    |||
    {Mobile App Development Trainee}%
    {Orange Digital Center}%
    {Jan 2025 - Mar 2025}%
    {%
        \item Completed 96-hour Flutter training mastering cross-platform development and state management.
    }%
    |||
    {Flutter Developer Intern}%
    {SlashHub}%
    {Oct 2024 - Jan 2025}%
    {%
        \item Designed reactive UI components for AI-powered e-commerce chatbot, implementing real-time messaging with 25\% user engagement improvement.
    }%
    |||%
}

% PROJECTS
\newcommand{\projectsList}{%
    {Jun 2025}%
    {https://github.com/KarimmYasser/isupply_app}%
    {i'Supply POS App - First Place Hackathon Winner}%
    {Developed a cross-platform \textbf{Flutter POS system} for desktop and mobile, featuring inventory search, cart management, checkout, and invoice tracking. Integrated \textbf{Hive} for local storage and \textbf{Supabase} for the back-end with offline synchronization.}%
    |||
    {Feb 2025 - Mar 2025}%
    {https://github.com/KarimmYasser/hangouts_crincale}%
    {Hangouts Crincale – Audio Analysis Tool}%
    {Engineered a professional-grade, cross-platform audio analysis application in \textbf{Flutter}, providing tools for frequency response visualization and parametric equalization.}%
    |||
    {Nov 2024 - Dec 2024}%
    {https://github.com/KarimmYasser/Slash-Fashion-Assistant-App}%
    {Fashion Assistant - E-commerce Platform}%
    {Built a personalized \textbf{Flutter} shopping assistant with AI-powered chatbot and product recommendation system.}%
    |||
    {Jun 2024 - July 2024}%
    {https://github.com/KarimmYasser/Cooking-up-application}%
    {Cooking Up App}%
    {Developed a \textbf{Flutter}-based recipe app with offline access using local storage, category filters, and interactive cooking tools.}%
    |||
    {Mar 2025 - May 2025}%
    {https://github.com/KarimmYasser/zengbary-app}%
    {Zengbary App}%
    {Developed a \textbf{Flutter} app to remotely control a microprocessor-based robot with HTTP communication.}%
    |||
    {Oct 2025 - Dec 2025}%
    {https://github.com/KarimmYasser/yapper-mobile}%
    {Yapper - X Clone Mobile App}%
    {Built a cross-platform \textbf{React Native} social media app with real-time WebSocket messaging, push notifications, RTL support, and CI/CD automation.}%
    |||
    {Aug 2025 - Sep 2025}%
    {https://github.com/KarimmYasser/coffee_shop}%
    {Coffee Shop Android App}%
    {Developed an offline-first Android app using Kotlin Jetpack Compose, Clean Architecture with MVVM, Hilt, Room, and Retrofit.}%
    |||
    {Aug 2025}%
    {https://github.com/KarimmYasser/recipe-box}%
    {RecipeBox Recipe Management App}%
    {Built an offline-first Android recipe app using Jetpack Compose, Clean Architecture (MVVM), Room, and Dagger/Hilt.}%
    |||
    {Nov 2025}%
    {https://github.com/KarimmYasser/Walmart-Sales-Forecasting-ML}%
    {Walmart Sales Forecasting - ML Pipeline}%
    {Developed an end-to-end ML pipeline achieving \textbf{99.96\% R²} accuracy, deployed via FastAPI and Streamlit with Docker.}%
    |||%
}

% TECHNICAL SKILLS
\newcommand{\programmingLanguages}{
Dart,
SQL,
Python,
Kotlin,
Java
}

\newcommand{\mobileDevelopment}{
Flutter (Mobile \& Desktop),
Cross-platform Development,
Responsive UI Design
}

\newcommand{\frameworksLibraries}{
Flutter Bloc,
Riverpod,
Provider,
GetX,
Firebase,
RESTful APIs,
Hive,
Dio,
GetIt,
Freezed,
GoRouter
}

\newcommand{\backendDatabase}{
Supabase,
Firebase,
SQLite,
Hive,
Offline-first Architecture,
API Integration
}

\newcommand{\developmentTools}{
Git,
GitHub,
VS Code,
Android Studio,
Postman,
Figma,
Agile/Scrum
}

\newcommand{\softwareEngineering}{
Clean Architecture,
SOLID Principles,
Dependency Injection,
State Management,
Object-Oriented Programming (OOP),
Design Patterns
}

\newcommand{\dataScience}{
Data Structures,
Algorithms
}

\newcommand{\artificialIntelligence}{
ML Integration (TFLite/ML Kit)
}

\newcommand{\researchSkills}{
Technical Documentation,
Code Review
}

\newcommand{\specializedSkills}{
Algorithms,
Data Structures,
ML Integration (TFLite/ML Kit)
}

% CORE COMPETENCIES
\newcommand{\problemSolving}{
Analytical thinking,
Problem decomposition,
Debugging,
Root cause identification
}

\newcommand{\leadership}{
Technical mentoring,
Code review,
Cross-functional collaboration,
Agile teamwork
}

\newcommand{\communication}{
Technical documentation,
Knowledge transfer,
Remote collaboration
}

\newcommand{\continuousLearning}{
Technology adoption,
Industry best practices,
Rapid skill acquisition
}

% ============================================================
