% ============================================================
% RESUME CONTENT - OPTIMIZED FOR ANDROID DEVELOPER ROLE
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
\textbf{Android Developer} with hands-on experience building native Android applications using \textbf{Kotlin}, \textbf{Jetpack Compose}, and modern Android architecture patterns. Proven expertise in \textbf{MVVM}, \textbf{Clean Architecture}, dependency injection (Hilt/Dagger), Room database, and RESTful API integration. Strong foundation in mobile development with cross-platform experience in Flutter and React Native. Passionate about creating performant, user-friendly mobile applications with clean, maintainable code.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{GPA: Excellent}

% WORK EXPERIENCE
\newcommand{\experienceList}{%
    {Android Developer Intern}%
    {Banque Misr}%
    {Jul 2025 - Sep 2025}%
    {%
        \item Developed native Android applications using Kotlin, Android Jetpack components, and the Room Database for local data persistence.
        \item Implemented MVVM architecture patterns to create scalable and maintainable mobile solutions with enhanced user experience and optimized performance.
    }%
    |||
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Dec 2025}%
    {%
        \item Won first place in a 30+ team hackathon, earning a full-time position offer.
        \item Collaborated with back-end engineers and QA testers in an agile environment, analyzing the application's architecture and state management to guide feature development.
        \item Implemented offline functionality and developed complex queries for the offline database, gaining hands-on experience in mobile data management.
    }%
    |||
    {Flutter Developer Intern}%
    {SlashHub}%
    {Oct 2024 - Jan 2025}%
    {%
        \item Designed reactive UI components for an AI-powered e-commerce chatbot, implementing real-time messaging and product recommendations.
        \item Achieved a 25\% improvement in user engagement metrics and significantly reduced bounce rates through optimized UI/UX flows.
    }%
    |||
    {Mobile Development Intern (Flutter \& ML)}%
    {Informatique}%
    {Jul 2025 - Aug 2025}%
    {%
        \item Integrated Machine Learning models into mobile applications using TFLite and ML Kit for on-device inference and real-time data processing.
    }%
    |||%
}

% PROJECTS
\newcommand{\projectsList}{%
    {Aug 2025 - Sep 2025}%
    {https://github.com/KarimmYasser/coffee_shop}%
    {Coffee Shop Android App}%
    {Developed an offline-first coffee shop app using \textbf{Kotlin Jetpack Compose}. Implemented \textbf{Clean Architecture} with \textbf{MVVM}, utilizing \textbf{Hilt} for dependency injection, \textbf{Room} for local persistence, and \textbf{Retrofit} for API integration.}%
    |||
    {Aug 2025}%
    {https://github.com/KarimmYasser/recipe-box}%
    {RecipeBox Recipe Management App}%
    {Developed a modern Android recipe application using \textbf{Jetpack Compose}, architected with \textbf{Clean Architecture (MVVM)}, \textbf{Room} database for offline access, and \textbf{Dagger/Hilt} for robust dependency management.}%
    |||
    {Jul 2025 - Aug 2025}%
    {https://github.com/KarimmYasser/fakestore-ecommerce-app}%
    {FakeStore E-Commerce App}%
    {Built an Android e-commerce application in \textbf{Kotlin}, demonstrating \textbf{Jetpack Compose} for reactive UI, \textbf{Paging 3} for efficient network data loading, and \textbf{Room} for local cart persistence.}%
    |||
    {Jul 2025}%
    {https://github.com/KarimmYasser/secure-notes}%
    {SecureNotes Android App}%
    {Developed a secure Android notes application using \textbf{Jetpack Compose} for the UI and \textbf{Proto DataStore} for type-safe, persistent settings management and local encryption.}%
    |||
    {Jun 2025}%
    {https://github.com/KarimmYasser/isupply_app}%
    {i'Supply POS App - Hackathon Winner}%
    {Developed a cross-platform POS system for mobile featuring \textbf{offline synchronization}, \textbf{Hive} local storage, and \textbf{Supabase} backend, seamlessly handling over 1000 products with complex filtering.}%
    |||%
}

% TECHNICAL SKILLS
\newcommand{\programmingLanguages}{Kotlin, Java, Dart, SQL, Python, TypeScript}
\newcommand{\mobileDevelopment}{Android Development (Kotlin, Jetpack Compose, XML Views), Flutter, Cross-platform Development}
\newcommand{\frameworksLibraries}{Dagger/Hilt, Android Navigation Component, Room, Retrofit, Coroutines/Flow, Paging 3, DataStore, WorkManager, Firebase, Flutter Bloc}
\newcommand{\backendDatabase}{Room, SQLite, Firebase, Supabase, Offline-first Architecture, RESTful API Integration}
\newcommand{\developmentTools}{}
\newcommand{\softwareEngineering}{Clean Architecture, MVVM, SOLID Principles, Dependency Injection, State Management, Object-Oriented Programming (OOP)}
\newcommand{\dataScience}{}
\newcommand{\artificialIntelligence}{}
\newcommand{\researchSkills}{}
\newcommand{\specializedSkills}{}

% CORE COMPETENCIES
\newcommand{\problemSolving}{Analytical thinking, Problem decomposition, Debugging, Memory leak profiling}
\newcommand{\leadership}{Technical mentoring, Code review, Cross-functional collaboration}
\newcommand{\communication}{Technical documentation, Knowledge transfer, Agile teamwork}
\newcommand{\continuousLearning}{Technology adoption, Android best practices, Rapid skill acquisition}
% ============================================================

