% ============================================================
% RESUME CONTENT - OPTIMIZED FOR STUDY SCHOLARSHIP APPLICATION
% ============================================================

% PERSONAL INFORMATION
\newcommand{\myName}{Karim Yasser}
\newcommand{\myLocation}{Cairo, Egypt}
\newcommand{\myEmail}{karimmyasserr@gmail.com}
\newcommand{\myPhone}{+201144432284}
\newcommand{\myGithub}{github.com/KarimmYasser}
\newcommand{\myGithubLink}{https://github.com/KarimmYasser}
\newcommand{\myLinkedin}{linkedin.com/in/karimmyasserr}
\newcommand{\myLinkedinLink}{https://www.linkedin.com/in/karimmyasserr/}
\newcommand{\myPortfolio}{Portfolio: karim-yasser.vercel.app}
\newcommand{\myPortfolioLink}{https://karim-yasser.vercel.app}

% SUMMARY
\newcommand{\mySummary}{%
Highly motivated \textbf{Computer Engineering} student at Cairo University with \textbf{Excellent GPA} and diverse technical expertise spanning software development, machine learning, and hardware design. IBM certified Data Scientist with proven leadership through teaching roles and hackathon victories. Demonstrated ability to excel academically while gaining extensive industry experience through multiple internships. Passionate about advancing computer engineering knowledge and contributing to cutting-edge research. Strong track record of initiative, self-learning, and delivering impactful projects across multiple domains.
}

% EDUCATION
\newcommand{\myDegree}{Bachelor of Engineering in \textbf{Computer Engineering}}
\newcommand{\myUniversity}{CAIRO UNIVERSITY, FACULTY OF ENGINEERING}
\newcommand{\myEducationDate}{Sep 2022 - Jun 2027}
\newcommand{\myGPA}{\textbf{GPA: Excellent}}

% WORK EXPERIENCE - Showing breadth of achievement
\newcommand{\experienceList}{%
    {Software Developer}%
    {I'SUPPLY}%
    {Jul 2025 - Present}%
    {%
        \item \textbf{Won first place} in a 30+ team hackathon, earning a full-time position offer.
        \item Developed scalable enterprise solutions demonstrating technical excellence.
    }%
    |||
    {Data Science Trainee}%
    {Digital Egypt Pioneers Initiative (DEPI)}%
    {Jun 2025 - Dec 2025}%
    {%
        \item Earned \textbf{IBM Data Scientist Professional Certificate} with comprehensive Python and ML training.
        \item Completed capstone project achieving 99.96\% R² accuracy in predictive modeling.
    }%
    |||
    {Android Developer Intern}%
    {Banque Misr}%
    {Jul 2025 - Aug 2025}%
    {%
        \item Selected for prestigious internship at Egypt's leading national bank.
        \item Developed banking applications applying Clean Architecture principles.
    }%
    |||
    {Mobile Development Intern (Flutter \& ML)}%
    {Informatique}%
    {Jul 2025 - Aug 2025}%
    {%
        \item Integrated Machine Learning models into production mobile applications.
    }%
    |||
    {Flutter Instructor}%
    {IEEE CU}%
    {Jun 2024 - Aug 2024}%
    {%
        \item Led Flutter curriculum development and \textbf{mentored aspiring developers}.
    }%
    |||
    {Session Lead}%
    {Udacity}%
    {Nov 2023 - Aug 2024}%
    {%
        \item Provided technical mentoring sessions supporting student success.
    }%
    |||
    {Research \& Development Member}%
    {Enactus}%
    {Jan 2024 - Present}%
    {%
        \item Contributing to social entrepreneurship initiatives with technology solutions.
    }%
    |||%
}

% PROJECTS - Demonstrating academic and technical breadth
\newcommand{\projectsList}{%
    {Nov 2025 - Dec 2025}%
    {https://github.com/KarimmYasser/VLSI-Convolution-Systolic-Accelerator}%
    {VLSI Convolution Systolic Accelerator}%
    {Designed a CNN hardware accelerator in Verilog demonstrating advanced \textbf{computer architecture} and \textbf{AI hardware} knowledge.}%
    |||
    {Nov 2025}%
    {https://github.com/KarimmYasser/Walmart-Sales-Forecasting-ML}%
    {Walmart Sales Forecasting ML Pipeline}%
    {Built end-to-end ML pipeline achieving \textbf{99.96\% R² accuracy} with MLOps deployment.}%
    |||
    {Mar 2024 - May 2024}%
    {https://github.com/KarimmYasser/stall_3alda2ery}%
    {5-Stage Pipelined MIPS Processor}%
    {Designed complete 32-bit processor with pipeline architecture and hazard handling.}%
    |||
    {Feb 2025}%
    {https://github.com/KarimmYasser/cmpsh}%
    {Unix Shell Implementation}%
    {Built functional Unix shell in C demonstrating \textbf{systems programming} expertise.}%
    |||
    {Mar 2025 – May 2025}%
    {https://github.com/KarimmYasser/sher-look}%
    {Sherlook Search Engine}%
    {Full-stack search engine processing 50K+ pages with ranking algorithms.}%
    |||
    {Nov 2024 - Dec 2024}%
    {https://github.com/KarimmYasser/Slash-Fashion-Assistant-App}%
    {Fashion Assistant Mobile App}%
    {AI-powered e-commerce app with NLP chatbot improving user engagement by 25\%.}%
    |||
    {Feb 2024 – Apr 2024}%
    {https://github.com/KarimmYasser/AES}%
    {FPGA AES-128 Encryption}%
    {Implemented cryptographic hardware on FPGA demonstrating \textbf{security engineering}.}%
    |||%
}

% TECHNICAL SKILLS - Comprehensive breadth
\newcommand{\programmingLanguages}{
Python,
C++,
C,
Dart,
Java,
JavaScript,
SQL,
Verilog,
VHDL
}

\newcommand{\mobileDevelopment}{
Flutter,
Android,
React Native,
Cross-platform Development
}

\newcommand{\frameworksLibraries}{
TensorFlow,
Scikit-learn,
FastAPI,
Flutter/Bloc,
Django
}

\newcommand{\backendDatabase}{
PostgreSQL,
MySQL,
Firebase,
Docker
}

\newcommand{\developmentTools}{
Git,
GitHub,
VS Code,
Linux,
Xilinx Vivado,
Android Studio
}

\newcommand{\softwareEngineering}{
Clean Architecture,
Design Patterns,
OOP,
Agile Methodology,
CI/CD
}

\newcommand{\dataScience}{
Machine Learning,
Data Analysis,
Statistical Modeling,
Data Visualization
}

\newcommand{\artificialIntelligence}{
Deep Learning,
NLP,
Computer Vision,
Hardware Acceleration
}

\newcommand{\researchSkills}{
\textbf{Research Methodology},
Technical Writing,
Literature Review,
Experimentation
}

\newcommand{\specializedSkills}{
\textbf{Computer Architecture},
VLSI Design,
FPGA Development,
Systems Programming,
Operating Systems
}

% CORE COMPETENCIES
\newcommand{\problemSolving}{
\textbf{Analytical thinking},
Research methodology,
Complex problem decomposition,
Innovation
}

\newcommand{\leadership}{
\textbf{Teaching \& mentoring},
Team collaboration,
Initiative,
Project management
}

\newcommand{\communication}{
\textbf{Technical presentation},
Academic writing,
Cross-functional collaboration
}

\newcommand{\continuousLearning}{
\textbf{Self-directed learning},
Research aptitude,
Technology adoption,
Academic excellence
}

% ============================================================
